---
title: "Creation of data files for analysis"
author: "Andrew Perfors"
output: html_document
---

This creates the data files we'll need for subsequent analyses.

```{r setup, include=FALSE}
# We'll begin by loading up the libraries and data we need, as always.
knitr::opts_chunk$set(echo = TRUE)

# loading the libraries
library(tidyverse)
library(here)
library(ggplot2)
library(gridExtra)
library(rminer)

# load the full datasets
de3raw <- read.csv(file=here("Experiment3_Andy.csv")) %>% as_tibble()
# remove people who failed the bot check
bad <- de3raw %>% filter(botCheck==0 | actuallyEstimated==0)
badpeople <- bad$pID
de3 <- de3raw %>% filter(!(pID %in% badpeople))
bad <- de3raw %>% filter(pID %in% badpeople)
de3$pID <- as.factor(de3$pID)

# write the two main datasets
write.csv(bad,"datafiles/exp3_bad_data.csv")
write.csv(de3,"datafiles/exp3_good_data.csv")

# split by condition
de3est <- de3 %>% filter(condition=="estimated")
de3given <- de3 %>% filter(condition=="given")

# make the priors all nonzero
de3aprior_long <- de3est %>%
  filter(section=="prior") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de3aprior_long$x <- as.numeric(str_sub(de3aprior_long$x,2,10))/100

de3aprior_long_adj <- de3aprior_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de3aprior_adj <- de3aprior_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de3aprior_old <- de3est %>% filter(section=="prior")
de3aprior_old <- de3aprior_old %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de3aprior_new <- merge(de3aprior_old,de3aprior_adj) %>%
  select(pID,condition,section,seenRed,seenBlue,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,time,
         chipsOrder,actuallyEstimated)

# make the posterior for estimated all nonzero
de3estpost_long <- de3est %>%
  filter(section=="posterior") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de3estpost_long$x <- as.numeric(str_sub(de3estpost_long$x,2,10))/100

de3estpost_long_adj <- de3estpost_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de3estpost_adj <- de3estpost_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de3estpost_old <- de3est %>% filter(section=="posterior")
de3estpost_old <- de3estpost_old %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de3estpost_new <- merge(de3estpost_old,de3estpost_adj) %>%
  select(pID,condition,section,seenRed,seenBlue,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,time,
         chipsOrder,actuallyEstimated)

de3est_adj <- rbind(de3aprior_new,de3estpost_new)

# make the posterior for given all nonzero
de3givenpost_long <- de3given %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de3givenpost_long$x <- as.numeric(str_sub(de3givenpost_long$x,2,10))/100

de3givenpost_long_adj <- de3givenpost_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de3givenpost_adj <- de3givenpost_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de3givenpost_old <- de3given %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de3given_adj <- merge(de3givenpost_old,de3givenpost_adj) %>%
  select(pID,condition,section,seenRed,seenBlue,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,time,
         chipsOrder,actuallyEstimated)

de3all_adj <- rbind(de3est_adj,de3given_adj)

write.csv(de3all_adj,"datafiles/exp3_all_data_adj.csv")

```


## ESTIMATED condition

This contains the code to fit individuals in four different ways. 

1. Fit $\beta$, $\gamma$, and $\delta$. Output is in `exp3est_allfits_adj.csv`

2. Fit beta and one variable ($\gamma$) which is the same for $\gamma$ and $\delta$, i.e., it enforces them to be the same. Output is in `exp3est_twofits_adj.csv`

3. Fit only $\beta$, and force $\gamma=\delta=1$. The point of this is to see if the fits we get on $\beta$ which imply they are ignoring the prior are an artefact of also fitting $\delta$ and $\gamma$. Output is in `exp3est_betafits_adj.csv`

4. Fit only $\gamma$, and assume that $\beta=1$. The point of this is the opposite of #3. Output is in `exp3est_gammafits_adj.csv`

```{r fitthingsestimated}
# uncomment this to make it do it on the adjusted dataset
de3all <- de3all_adj

de3est_long <- de3all %>%
  filter(condition=="estimated") %>%
  select(-c(condition,age,gender,botCheck,time,chipsOrder,
            actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="y")
de3est_long$x <- as.numeric(str_sub(de3est_long$x,2,10))/100

# the function that fits beta, gamma, and delta
frestall <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
  dprior <- d %>% filter(section=="prior")
   beta <- ps[1]
   gamma <- ps[2]
   delta <- ps[3]
   x <- dpost$x
   y <- dpost$y
   pry <- dprior$y
   y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(delta*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits beta and gamma/delta as one
fresttwo <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
  dprior <- d %>% filter(section=="prior")
   beta <- ps[1]
   gamma <- ps[2]
   x <- dpost$x
   y <- dpost$y
   pry <- dprior$y
      y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only beta
frestbeta <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
  dprior <- d %>% filter(section=="prior")
  gamma <- 1
   beta <- ps[1]
   x <- dpost$x
   y <- dpost$y
   pry <- dprior$y
    y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only gamma
frestgamma <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
  dprior <- d %>% filter(section=="prior")
   gamma <- ps[1]
   x <- dpost$x
   y <- dpost$y
   pry <- dprior$y
      y <- y/sum(y)
   pry <- pry/sum(pry)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- pry
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# fitting delta, gamma, and beta
ddestall <- de3est_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1,1),frestall,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001,0.0000001),
                          upper=c(0.9999999,50,50))))

de3est_allfits <- de3all %>% 
  filter(condition=="estimated") %>% 
  filter(section=="posterior")
de3est_allfits$beta <- NA
de3est_allfits$gamma <- NA
de3est_allfits$delta <- NA
de3est_allfits$value <- NA

for (i in 1:nrow(de3est_allfits)) {
  pid <- ddestall$pID[i]
  de3est_allfits$beta[de3est_allfits$pID==pid] <-
    ddestall$fit[[i]]$par[1]
  de3est_allfits$gamma[de3est_allfits$pID==pid] <-
    ddestall$fit[[i]]$par[2]
  de3est_allfits$delta[de3est_allfits$pID==pid] <-
    ddestall$fit[[i]]$par[3]
  de3est_allfits$value[de3est_allfits$pID==pid] <-
    ddestall$fit[[i]]$value[1]
}

write.csv(de3est_allfits,"datafiles/exp3est_allfits_adj.csv")

# fitting delta/gamma, and beta
ddesttwo <- de3est_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),fresttwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

de3est_twofits <- de3all %>% 
  filter(condition=="estimated") %>% 
  filter(section=="posterior")
de3est_twofits$beta <- NA
de3est_twofits$gamma <- NA
de3est_twofits$value <- NA

for (i in 1:nrow(de3est_twofits)) {
  pid <- ddesttwo$pID[i]
  de3est_twofits$beta[de3est_twofits$pID==pid] <-
    ddesttwo$fit[[i]]$par[1]
  de3est_twofits$gamma[de3est_twofits$pID==pid] <-
    ddesttwo$fit[[i]]$par[2]
  de3est_twofits$value[de3est_twofits$pID==pid] <-
    ddesttwo$fit[[i]]$value[1]
}

write.csv(de3est_twofits,"datafiles/exp3est_twofits_adj.csv")


# fitting only beta
ddestbeta <- de3est_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5),frestbeta,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(0.9999999))))

de3est_betafits <- de3all %>% 
  filter(condition=="estimated") %>% 
  filter(section=="posterior")
de3est_betafits$beta <- NA
de3est_betafits$value <- NA

for (i in 1:nrow(de3est_betafits)) {
  pid <- ddestbeta$pID[i]
  de3est_betafits$beta[de3est_betafits$pID==pid] <-
    ddestbeta$fit[[i]]$par[1]
  de3est_betafits$value[de3est_betafits$pID==pid] <-
    ddestbeta$fit[[i]]$value[1]
}

write.csv(de3est_betafits,"datafiles/exp3est_betafits_adj.csv")

# fitting only gamma
ddestgamma <- de3est_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1),frestgamma,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(50))))

de3est_gammafits <- de3all %>% 
  filter(condition=="estimated") %>% 
  filter(section=="posterior")
de3est_gammafits$gamma <- NA
de3est_gammafits$value <- NA

for (i in 1:nrow(de3est_gammafits)) {
  pid <- ddestgamma$pID[i]
  de3est_gammafits$gamma[de3est_gammafits$pID==pid] <-
    ddestgamma$fit[[i]]$par[1]
  de3est_gammafits$value[de3est_gammafits$pID==pid] <-
    ddestgamma$fit[[i]]$value[1]
}

write.csv(de3est_gammafits,"datafiles/exp3est_gammafits_adj.csv")
```

Now we're going to do the same thing with the GIVEN data. In this people were given the prior so we fit posteriors assuming that as their prior. As before there are four possibilities.

1. Fit $\beta$, $\gamma$, and $\delta$. Output is in `exp3given_allfits_adj.csv`

2. Fit beta and one variable ($\gamma$) which is the same for $\gamma$ and $\delta$, i.e., it enforces them to be the same. Output is in `exp3given_twofits_adj.csv`

3. Fit only $\beta$, and force $\gamma=\delta=1$. The point of this is to see if the fits we get on $\beta$ which imply they are ignoring the prior are an artefact of also fitting $\delta$ and $\gamma$. Output is in `exp3given_betafits_adj.csv`

4. Fit only $\gamma$, and assume that $\beta=1$. The point of this is the opposite of #3. Output is in `exp3given_gammafits_adj.csv`


```{r fitthingsgiven}
de3given_long <- de3all %>%
  filter(condition=="given") %>%
  select(-c(condition,age,gender,botCheck,time,chipsOrder,
            actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="y")
de3given_long$x <- as.numeric(str_sub(de3given_long$x,2,10))/100

# the function that fits beta, gamma, and delta
frgivenall <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
   beta <- ps[1]
   gamma <- ps[2]
   delta <- ps[3]
   x <- dpost$x
   y <- dpost$y
   pry <- c(0.043561,0.049242,0.064394,0.104167,0.132576,0.212121,
            0.132576,0.104167,0.064394,0.049242,0.043561)
   y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(delta*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits beta and gamma/delta as one
frgiventwo <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
   beta <- ps[1]
   gamma <- ps[2]
   x <- dpost$x
   y <- dpost$y
    pry <- c(0.043561,0.049242,0.064394,0.104167,0.132576,0.212121,
            0.132576,0.104167,0.064394,0.049242,0.043561)
      y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only beta
frgivenbeta <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
  gamma <- 1
   beta <- ps[1]
   x <- dpost$x
   y <- dpost$y
      pry <- c(0.043561,0.049242,0.064394,0.104167,0.132576,0.212121,
            0.132576,0.104167,0.064394,0.049242,0.043561)
    y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only gamma
frgivengamma <- function(ps,d) {
  dpost <- d %>% filter(section=="posterior")
   gamma <- ps[1]
   x <- dpost$x
   y <- dpost$y
      pry <- c(0.043561,0.049242,0.064394,0.104167,0.132576,0.212121,
            0.132576,0.104167,0.064394,0.049242,0.043561)
      y <- y/sum(y)
   pry <- pry/sum(pry)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- pry
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# fitting delta, gamma, and beta
ddgivenall <- de3given_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1,1),frgivenall,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001,0.0000001),
                          upper=c(0.9999999,50,50))))

de3given_allfits <- de3all %>% 
  filter(condition=="given") 
de3given_allfits$beta <- NA
de3given_allfits$gamma <- NA
de3given_allfits$delta <- NA
de3given_allfits$value <- NA

for (i in 1:nrow(de3given_allfits)) {
  pid <- ddgivenall$pID[i]
  de3given_allfits$beta[de3given_allfits$pID==pid] <-
    ddgivenall$fit[[i]]$par[1]
  de3given_allfits$gamma[de3given_allfits$pID==pid] <-
    ddgivenall$fit[[i]]$par[2]
  de3given_allfits$delta[de3given_allfits$pID==pid] <-
    ddgivenall$fit[[i]]$par[3]
  de3given_allfits$value[de3given_allfits$pID==pid] <-
    ddgivenall$fit[[i]]$value[1]
}

write.csv(de3given_allfits,"datafiles/exp3given_allfits_adj.csv")

# fitting delta/gamma, and beta
ddgiventwo <- de3given_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),frgiventwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

de3given_twofits <- de3all %>% 
  filter(condition=="given") 
de3given_twofits$beta <- NA
de3given_twofits$gamma <- NA
de3given_twofits$value <- NA

for (i in 1:nrow(de3given_twofits)) {
  pid <- ddgiventwo$pID[i]
  de3given_twofits$beta[de3given_twofits$pID==pid] <-
    ddgiventwo$fit[[i]]$par[1]
  de3given_twofits$gamma[de3given_twofits$pID==pid] <-
    ddgiventwo$fit[[i]]$par[2]
  de3given_twofits$value[de3given_twofits$pID==pid] <-
    ddgiventwo$fit[[i]]$value[1]
}

write.csv(de3given_twofits,"datafiles/exp3given_twofits_adj.csv")


# fitting only beta
ddgivenbeta <- de3given_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5),frgivenbeta,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(0.9999999))))

de3given_betafits <- de3all %>% 
  filter(condition=="given") 
de3given_betafits$beta <- NA
de3given_betafits$value <- NA

for (i in 1:nrow(de3given_betafits)) {
  pid <- ddgivenbeta$pID[i]
  de3given_betafits$beta[de3given_betafits$pID==pid] <-
    ddgivenbeta$fit[[i]]$par[1]
  de3given_betafits$value[de3given_betafits$pID==pid] <-
    ddgivenbeta$fit[[i]]$value[1]
}

write.csv(de3given_betafits,"datafiles/exp3given_betafits_adj.csv")

# fitting only gamma
ddgivengamma <- de3given_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1),frgivengamma,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(50))))

de3given_gammafits <- de3all %>% 
  filter(condition=="given") 
de3given_gammafits$gamma <- NA
de3given_gammafits$value <- NA

for (i in 1:nrow(de3given_gammafits)) {
  pid <- ddgivengamma$pID[i]
  de3given_gammafits$gamma[de3given_gammafits$pID==pid] <-
    ddgivengamma$fit[[i]]$par[1]
  de3given_gammafits$value[de3given_gammafits$pID==pid] <-
    ddgivengamma$fit[[i]]$value[1]
}

write.csv(de3given_gammafits,"datafiles/exp3given_gammafits_adj.csv")
```



## Calculate aggregate best-fit parameters

This contains the code for the aggregate best fits in different ways. First we'll do it just for ESTIMATED, then for GIVEN. It does it for each for all of the four possibilities above. 

```{r fitthingsaggregate}
# make dataset with aggregate results
de3est_long <- de3all %>%
  filter(condition=="estimated") %>%
  select(-c(condition,age,gender,botCheck,time,chipsOrder,
            actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="pry")
de3est_long$x <- as.numeric(str_sub(de3est_long$x,2,10))/100


de3est_lsum <- de3est_long %>%
  group_by(section,x) %>%
  summarise(y=mean(pry)) %>%
  ungroup()

write.csv(de3est_lsum,"datafiles/exp3est_aggregate_curves_adj.csv")

# fitting delta, gamma, and beta on estimated
ddaggall_est <- optim(c(0.5,1,1),frestall,d=de3est_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001,0.0000001),
                  upper=c(0.9999999,50,50))

# fitting gamma and beta on estimated
ddaggtwo_est <- optim(c(0.5,1),fresttwo,d=de3est_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001),
                  upper=c(0.9999999,50))

# fitting beta on estimated
ddaggbeta_est <- optim(c(0.5),frestbeta,d=de3est_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(0.9999999))

# fitting gamma on estimated
ddagggamma_est <- optim(c(1),frestgamma,d=de3est_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(50))

# now get given
de3given_long <- de3all %>%
  filter(condition=="given") %>%
  select(-c(condition,age,gender,botCheck,time,chipsOrder,
            actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="pry")
de3given_long$x <- as.numeric(str_sub(de3given_long$x,2,10))/100


de3given_lsum <- de3given_long %>%
  group_by(section,x) %>%
  summarise(y=mean(pry)) %>%
  ungroup()

# fitting delta, gamma, and beta on estimated
ddaggall_given <- optim(c(0.5,1,1),frgivenall,d=de3given_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001,0.0000001),
                  upper=c(0.9999999,50,50))

# fitting gamma and beta on estimated
ddaggtwo_given <- optim(c(0.5,1),frgiventwo,d=de3given_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001),
                  upper=c(0.9999999,50))

# fitting beta on estimated
ddaggbeta_given <- optim(c(0.5),frgivenbeta,d=de3given_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(0.9999999))

# fitting gamma on estimated
ddagggamma_given <- optim(c(1),frgivengamma,d=de3given_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(50))

write.csv(de3given_lsum,"datafiles/exp3given_aggregate_curves_adj.csv")


condition <- c(rep("estimated",4),rep("given",4))
fitted <- c("all","two","beta","gamma","all","two","beta","gamma")
beta <- c(ddaggall_est$par[1],ddaggtwo_est$par[1],ddaggbeta_est$par[1],NA,
          ddaggall_given$par[1],ddaggtwo_given$par[1],ddaggbeta_given$par[1],NA)
gamma <- c(ddaggall_est$par[2],ddaggtwo_est$par[2],NA,ddagggamma_est$par[1],
          ddaggall_given$par[2],ddaggtwo_given$par[2],NA,ddagggamma_given$par[1])
delta <- c(ddaggall_est$par[3],NA,NA,NA,ddaggall_given$par[3],NA,NA,NA)
value <- c(ddaggall_est$value,ddaggtwo_est$value,ddaggbeta_est$value,
           ddagggamma_est$value,ddaggall_given$value,ddaggtwo_given$value,
           ddaggbeta_given$value,ddagggamma_given$value)
dagg <- tibble(condition,fitted,beta,gamma,delta,value)
write.csv(dagg,"datafiles/exp3all_aggregate_fits_adj.csv")
```