---
title: "Analyses of main data: Experiment 3"
author: "Andrew Perfors"
output: html_document
---


```{r setup, include=FALSE}
# We'll begin by loading up the libraries and data we need, as always.
knitr::opts_chunk$set(echo = TRUE)

# loading the libraries
library(tidyverse)
library(here)
library(ggplot2)
library(gridExtra)
library(plotly)

# load the full datasets
de3all <- read.csv(file=here("datafiles/exp3_all_data_adj.csv")) %>% as_tibble()
de3all$pID <- as.factor(de3all$pID)
de3all$condition <- as.factor(de3all$condition)
levels(de3all$condition) <- c("Esᴛɪᴍᴀᴛᴇᴅ", "Gɪᴠᴇɴ")
de3given <- de3all %>% filter(condition=="Gɪᴠᴇɴ")
de3est <- de3all %>% filter(condition=="Esᴛɪᴍᴀᴛᴇᴅ")
Ne <- nrow(de3est)/2
Ng <- nrow(de3given)

# load the fitted data
de3e_fitall <- read.csv(file=here("datafiles/exp3est_allfits_adj.csv")) %>% as_tibble()
de3e_fittwo <- read.csv(file=here("datafiles/exp3est_twofits_adj.csv")) %>% as_tibble()
de3e_fitbeta <- read.csv(file=here("datafiles/exp3est_betafits_adj.csv")) %>% as_tibble()
de3e_fitgamma <- read.csv(file=here("datafiles/exp3est_gammafits_adj.csv")) %>% as_tibble()
de3g_fitall <- read.csv(file=here("datafiles/exp3given_allfits_adj.csv")) %>% as_tibble()
de3g_fittwo <- read.csv(file=here("datafiles/exp3given_twofits_adj.csv")) %>% as_tibble()
de3g_fitbeta <- read.csv(file=here("datafiles/exp3given_betafits_adj.csv")) %>% as_tibble()
de3g_fitgamma <- read.csv(file=here("datafiles/exp3given_gammafits_adj.csv")) %>% as_tibble()

# convert "value" to mean squared error
de3e_fitall$value <- de3e_fitall$value/11
de3e_fitbeta$value <- de3e_fitbeta$value/11
de3e_fittwo$value <- de3e_fittwo$value/11
de3e_fitgamma$value <- de3e_fitgamma$value/11
de3g_fitall$value <- de3g_fitall$value/11
de3g_fitbeta$value <- de3g_fitbeta$value/11
de3g_fittwo$value <- de3g_fittwo$value/11
de3g_fitgamma$value <- de3g_fitgamma$value/11

# rename
de3g_fitall$condition <- as.factor(de3g_fitall$condition)
levels(de3g_fitall$condition) <- c("Gɪᴠᴇɴ")
de3g_fitbeta$condition <- as.factor(de3g_fitbeta$condition)
levels(de3g_fitbeta$condition) <- c("Gɪᴠᴇɴ")
de3g_fittwo$condition <- as.factor(de3g_fittwo$condition)
levels(de3g_fittwo$condition) <- c("Gɪᴠᴇɴ")
de3g_fitgamma$condition <- as.factor(de3g_fitgamma$condition)
levels(de3g_fitgamma$condition) <- c("Gɪᴠᴇɴ")
de3e_fitall$condition <- as.factor(de3e_fitall$condition)
levels(de3e_fitall$condition) <- c("Esᴛɪᴍᴀᴛᴇᴅ")
de3e_fitbeta$condition <- as.factor(de3e_fitbeta$condition)
levels(de3e_fitbeta$condition) <- c("Esᴛɪᴍᴀᴛᴇᴅ")
de3e_fittwo$condition <- as.factor(de3e_fittwo$condition)
levels(de3e_fittwo$condition) <- c("Esᴛɪᴍᴀᴛᴇᴅ")
de3e_fitgamma$condition <- as.factor(de3e_fitgamma$condition)
levels(de3e_fitgamma$condition) <- c("Esᴛɪᴍᴀᴛᴇᴅ")

# combine datasets
de3_fitall <- rbind(de3e_fitall,de3g_fitall)
de3_fitbeta <- rbind(de3e_fitbeta,de3g_fitbeta)
de3_fittwo <- rbind(de3e_fittwo,de3g_fittwo)
de3_fitgamma <- rbind(de3e_fitgamma,de3g_fitgamma)
```

## First, comparing the prior

Our first question is what the estimated prior looked like, and how similar it was in aggregate to the one GIVEN to them. Looks like they are very similar, so yay!

```{r exp3_priors, echo=FALSE,fig.height=3, fig.width=4}
# make longer form
de3eprior_long <- de3est %>%
  filter(section=="prior") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de3eprior_long$x <- as.numeric(str_sub(de3eprior_long$x,2,10))/100

# make summary dataset for graphing
de3eprior_lsum <- de3eprior_long %>%
  group_by(x) %>%
  summarise(mean=mean(pry),
            sd=sd(pry),
            n=n(),
            sderr = sd/sqrt(n)) %>%
  ungroup()

pry <- c(0.043561,0.049242,0.064394,0.104167,0.132576,0.212121,
            0.132576,0.104167,0.064394,0.049242,0.043561)
pry <- pry/sum(pry)
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
de3givenprior <- tibble(x,pry)

p <- de3eprior_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  geom_jitter(data=de3eprior_long,mapping=aes(x=x,y=pry),
              alpha=0.1,colour="darkred") +
  geom_line(colour="darkred") + 
  geom_line(data=de3givenprior,mapping=aes(x=x,y=pry),linetype="dashed",
            colour="black") +
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="darkred") +
  theme_bw() +
  labs(title = "Pʀɪᴏʀ",x="Proportion of red",y="Probability")

p
ggsave("figures/exp3_priors_all_adj.png",plot=p,device="png",
       width=8,height=6, units="cm")
```

## Next, comparing the posteriors

Now we want to look at the aggregate posterior results in the ESTIMATED vs GIVEN conditions. Looks like they may be using the prior a bit more when it is GIVEN!


```{r exp3all_posteriors, echo=FALSE,fig.height=3, fig.width=8}
# make longer form
de3est_long <- de3est %>%
  filter(section=="posterior") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="fy")
de3est_long$x <- as.numeric(str_sub(de3est_long$x,2,10))/100

# make summary dataset for graphing
de3est_lsum <- de3est_long %>%
  group_by(x) %>%
  summarise(mean=mean(fy),
            sd=sd(fy),
            n=n(),
            sderr = sd/sqrt(n)) %>%
  ungroup()

allest <- de3est_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  geom_jitter(data=de3est_long,mapping=aes(x=x,y=fy),alpha=0.1,
              colour="mediumpurple4") +
  geom_line(colour="mediumpurple4") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple4") +
  theme_bw() +
  labs(title = "Esᴛɪᴍᴀᴛᴇᴅ",x="Proportion of red",y="Probability")

# make longer form
de3given_long <- de3given %>%
  filter(section=="posterior") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="fy")
de3given_long$x <- as.numeric(str_sub(de3given_long$x,2,10))/100

# make summary dataset for graphing
de3given_lsum <- de3given_long %>%
  group_by(x) %>%
  summarise(mean=mean(fy),
            sd=sd(fy),
            n=n(),
            sderr = sd/sqrt(n)) %>%
  ungroup()

allgiven <- de3given_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  geom_jitter(data=de3given_long,mapping=aes(x=x,y=fy),alpha=0.1,
              colour="mediumpurple3") +
  geom_line(colour="mediumpurple3") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple3") +
  theme_bw() +
  labs(title = "Gɪᴠᴇɴ",x="Proportion of red",y="Probability")


p <- grid.arrange(allest,allgiven,ncol=2)
ggsave("figures/exp3_posteriors_all_adj.png",plot=p,device="png",
       width=16,height=6, units="cm")
```



# Looking at fitted values: $\beta$, $\delta$, and $\gamma$

Let's have a look at the distribution of parameters in Experiment 3. As a reminder:

$\beta$: determines to what degree participants use their stated prior, and to what degree they use the uniform distribution to deduce their posterior. If $\beta=1$ that means it's all prior, if $\beta=0$ it is all uniform distribution

$\gamma$: how much they weighted the red chips they saw. if $\gamma=1$ it is veridical, lower is underweighting, higher is overweighting. 

$\delta$: how much they weighted the blue chips they saw. if $\delta=1$ it is veridical, lower is underweighting, higher is overweighting. 

```{r viewdatascatall, echo=FALSE, fig.height=8}
psbg <- de3_fitall %>%
  ggplot(mapping=aes(x=beta,y=gamma,colour=delta)) +
  geom_point(alpha=0.7,size=2) + 
  theme_bw() +
  facet_wrap(~condition) +
  labs(title = "\u03b2 vs \u03b3",x="\u03b2",y="\u03b3")

psbd <- de3_fitall %>%
  ggplot(mapping=aes(x=beta,y=delta,colour=gamma)) +
  geom_point(alpha=0.7,size=2) + 
  theme_bw() +
  facet_wrap(~condition) +
  labs(title = "\u03b2 vs \u03b4",x="\u03b2",y="\u03b4")

psgd <- de3_fitall %>%
  ggplot(mapping=aes(x=gamma,y=delta,colour=beta)) +
  geom_point(alpha=0.7,size=2) + 
  theme_bw() +
  facet_wrap(~condition) +
  labs(title = "\u03b3 vs \u03b4",x="\u03b3",y="\u03b4")

grid.arrange(psbg,psbd,psgd,nrow=3)
```

And also a 3D plot

```{r viewdata3dall, echo=FALSE, fig.height=4}
p <- plot_ly(x=de3_fitall$beta, y=de3_fitall$gamma, z=de3_fitall$delta,
             type="scatter3d",mode="markers", color=de3_fitall$beta)
p <- layout(p, scene = list(xaxis = list(title="\u03b2"),
                            yaxis = list(title = "\u03b3"),
                            zaxis = list(title="\u03b4")))
p
```

Finally, let's look at histograms of all of the variables.

```{r histallfits, echo=FALSE, fig.height=8}
pb <- de3_fitall %>%
  ggplot(mapping=aes(x=beta,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.1,show.legend=FALSE) + 
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b2",x="\u03b2",y="# of people")

pg <- de3_fitall %>%
  ggplot(mapping=aes(x=log(gamma),fill=condition)) +
    geom_histogram(alpha=0.7,colour="black",binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b3",x="log(\u03b3)",y="# of people")

pd <- de3_fitall %>%
  ggplot(mapping=aes(x=log(delta),fill=condition)) +
    geom_histogram(alpha=0.7,colour="black",binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b4",x="log(\u03b4)",y="# of people")

p <- grid.arrange(pb,pg,pd,ncol=3)
ggsave("figures/exp3_beta_gamma_delta_histograms_adj.png",plot=p,device="png",
       width=24,height=10, units="cm")

```

# Looking at fitted values: beta alone

I wanted to see if the beta values would be different if we weren't also fitting delta and gamma. So let's look at that histogram.

```{r histbetafits, echo=FALSE, fig.height=4}
pbeta <- de3_fitbeta %>%
  ggplot(mapping=aes(x=beta,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.1,show.legend=FALSE) + 
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b2 only",x="\u03b2",y="# of people")

pbeta
ggsave("figures/exp3_beta_histograms_adj.png",plot=pbeta,device="png",
       width=8,height=10, units="cm")

# percent less than 0.1
pl3e <- round(100*sum(de3_fitbeta$beta[de3_fitbeta$condition=="Esᴛɪᴍᴀᴛᴇᴅ"]<0.1)/Ne,1)
pl3g <- round(100*sum(de3_fitbeta$beta[de3_fitbeta$condition=="Gɪᴠᴇɴ"]<0.1)/Ng,1)
# percent greater than 0.9
pg3e <- round(100*sum(de3_fitbeta$beta[de3_fitbeta$condition=="Esᴛɪᴍᴀᴛᴇᴅ"]>0.9)/Ne,1)
pg3g <- round(100*sum(de3_fitbeta$beta[de3_fitbeta$condition=="Gɪᴠᴇɴ"]>0.9)/Ng,1)
```

For the priors: `r pl3e`% in ESTIMATED and `r pl3g`% in GIVEN had $\beta$ less than 0.1, and `r pg3e`% in ESTIMATED and `r pg3g`% in GIVEN had $\beta$ greater than 0.9.

# Looking at fitted values: $\gamma$ alone

I wanted to see if the $\gamma$ values would be different if we weren't also fitting $\delta$ and $\beta$ So let's look at that histogram.

```{r histgammafits, echo=FALSE, fig.height=4}
pgamma <- de3_fitgamma %>%
  ggplot(mapping=aes(x=log(gamma),fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b3 only",x="log(\u03b3)",y="# of people")

pgamma
ggsave("figures/exp3_gamma_histograms_adj.png",plot=pgamma,device="png",
       width=8,height=10, units="cm")

p <- grid.arrange(pbeta,pgamma,ncol=2)
ggsave("figures/exp3_combined_histograms_adj.png",plot=p,device="png",
       width=16,height=10, units="cm")

# likelihood percent less than 1
pll3g <- round(100*sum(de3_fitgamma$gamma[de3_fitgamma$condition=="Gɪᴠᴇɴ"]<1)/Ng,1)
pll3e <- round(100*sum(de3_fitgamma$gamma[de3_fitgamma$condition=="Esᴛɪᴍᴀᴛᴇᴅ"]<1)/Ne,1)

```

For the likelihoods: `r pll3g`% in GIVEN and `r pll3e`% in ESTIMATED had $\gamma$ less than 1 (i.e., were conservative).

# Looking at fitted values: $\beta$ and $\gamma$ alone

Here we assume one parameter (call it $\gamma$) instead of two separate ones ($\gamma$ and $\delta$). i.e. this forces them to be the same and can be thought of as a conservatism parameter. I wanted to look at this because I think it might be a lot more interpretable than having both.

$\beta$: determines to what degree participants use their stated prior, and to what degree they use the uniform distribution to deduce their posterior. If $\beta=1$ that means it's all prior, if $\beta=0$ it is all uniform distribution

$\gamma$: how much they weighted the chips they saw. if $\gamma=1$ it is veridical, lower is underweighting, higher is overweighting. 

```{r viewdatascattwo, echo=FALSE, fig.height=4}
p <- de3_fittwo %>%
  ggplot(mapping=aes(x=beta,y=log(gamma),colour=condition)) +
  geom_point(alpha=0.6,size=3,show.legend=FALSE) + 
  scale_colour_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition) +
  theme_bw() +
  labs(title = "\u03b2 vs \u03b3",x="\u03b2",y="log(\u03b3)")

p
ggsave("figures/exp3_beta_gamma_fitted_values_adj.png",plot=p,device="png",
       width=16,height=6, units="cm")
```

Let's calculate the Spearman correlation:

```{r correlationbetagamma}

# estimated
cor.test(de3_fittwo$beta[de3_fittwo$condition=="Esᴛɪᴍᴀᴛᴇᴅ"],
         de3_fittwo$gamma[de3_fittwo$condition=="Esᴛɪᴍᴀᴛᴇᴅ"],
         method="spearman")

# given
cor.test(de3_fittwo$beta[de3_fittwo$condition=="Gɪᴠᴇɴ"],
         de3_fittwo$gamma[de3_fittwo$condition=="Gɪᴠᴇɴ"],
         method="spearman")
```

And a histogram of them too

```{r histtwofits, echo=FALSE, fig.height=6}
pb <- de3_fittwo %>%
  ggplot(mapping=aes(x=beta,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.1,show.legend=FALSE) + 
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b2",x="\u03b2",y="# of people")

pg <- de3_fittwo %>%
  ggplot(mapping=aes(x=log(gamma),fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b3",x="log(\u03b3)",y="# of people")

p <- grid.arrange(pb,pg,ncol=2)
ggsave("figures/exp3_beta_gamma_histograms_adj.png",plot=p,device="png",
       width=16,height=10, units="cm")

# percent less than 0.1
pl3e <- round(100*sum(de3_fittwo$beta[de3_fittwo$condition=="Esᴛɪᴍᴀᴛᴇᴅ"]<0.1)/Ne,1)
pl3g <- round(100*sum(de3_fittwo$beta[de3_fittwo$condition=="Gɪᴠᴇɴ"]<0.1)/Ng,1)
# percent greater than 0.9
pg3e <- round(100*sum(de3_fittwo$beta[de3_fittwo$condition=="Esᴛɪᴍᴀᴛᴇᴅ"]>0.9)/Ne,1)
pg3g <- round(100*sum(de3_fittwo$beta[de3_fittwo$condition=="Gɪᴠᴇɴ"]>0.9)/Ng,1)

# likelihood percent less than 1
pll3g <- round(100*sum(de3_fittwo$gamma[de3_fittwo$condition=="Gɪᴠᴇɴ"]<1)/Ng,1)
pll3e <- round(100*sum(de3_fittwo$gamma[de3_fittwo$condition=="Esᴛɪᴍᴀᴛᴇᴅ"]<1)/Ne,1)

```

For the priors: `r pl3e`% in ESTIMATED and `r pl3g`% in GIVEN had $\beta$ less than 0.1, and `r pg3e`% in ESTIMATED and `r pg3g`% in GIVEN had $\beta$ greater than 0.9.

For the likelihoods: `r pll3g`% in GIVEN and `r pll3e`% in ESTIMATED had $\gamma$ less than 1 (i.e., were conservative).

# Individuals: ESTIMATED condition

So now let's look at individuals - compare their prior and posterior after five, based on the best-fit $\beta$ and $\gamma$ 

*red line*: their reported prior

*dark purple line*: their reported posterior

*solid grey*: Bayes rule prediction assuming their prior 

*dotted black*: line based on best-fit $\beta$ and $\gamma$

```{r individual_people_betagamma, echo=FALSE, fig.height=40}
ftps <- de3e_fittwo %>% select(pID,beta,gamma,value)
de3eprior_long_ps <- merge(de3eprior_long,ftps) 

de3epriorpr_long <- de3eprior_long_ps %>%
  group_by(pID) %>%
  mutate(prpy = pry*(x^4)*(1-x)) %>%
  mutate(ppy = prpy/sum(prpy)) %>%
  mutate(prpybest = (beta*pry+(1-beta)*rep(1/11,11))*
           (x^(gamma*4)*(1-x)^gamma)) %>%
  mutate(ppyb = prpybest/sum(prpybest)) %>%
  ungroup() %>%
  select(pID,x,pry,ppy,ppyb,beta,gamma,value)

x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
y <- x^4*(1-x)
de3est_long$py <- rep(y/sum(y),Ne)

de3e_long <- merge(de3epriorpr_long,de3est_long)

de3e_long_ps <- de3e_long %>%
  arrange(gamma,beta) %>%
  mutate(name = paste0("\u03b2=",round(beta,digits=2),
                       ", \u03b3=",round(gamma,digits=2),
                       "\n MSE=",round(value,digits=4),
                       " [",pID,"]"))

p <- de3e_long_ps %>%
  ggplot(mapping=aes(x=x, y=pry)) +
  #geom_line(mapping=aes(x=x,y=py),linetype="dotted",colour="darkgray") +
  geom_line(mapping=aes(x=x,y=ppy),linetype="solid",colour="darkgray") +
  geom_line(mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(colour="darkred") + 
  geom_line(mapping=aes(x=x,y=fy),colour="mediumpurple4") +
  #geom_line(mapping=aes(x=unx,y=uny),colour="dodgerblue4") +
  theme_bw() +
  facet_wrap(~name,ncol=8) +
  labs(title = "Individual fits, Esᴛɪᴍᴀᴛᴇᴅ: \u03b2 and \u03b3")

p

ggsave("figures/exp3_beta_gamma_indiv_fits_est_adj.png",plot=p,device="png",
       width=40,height=50, units="cm")

# look at the correlations between predicted and reported posteriors
de3epreds <- de3epriorpr_long %>% 
  group_by(pID) %>% 
  summarise(r = cor.test(ppy,ppyb)$estimate[[1]], 
            p = cor.test(ppy,ppyb)$p.value[[1]]) %>%
  ungroup()
```

# Individuals: GIVEN condition

We're going to do the same thing as before but this time with people in the GIVEN condition  

*red line*: the given prior

*dark blue line*: their reported posterior after unlimited

*solid grey*: Bayes rule prediction assuming the given prior 

*dotted black*: line based on best-fit $\beta$ and $\gamma$

```{r individual_people_betagamma_given, echo=FALSE, fig.height=40}
pry <- c(0.043561,0.049242,0.064394,0.104167,0.132576,0.212121,
            0.132576,0.104167,0.064394,0.049242,0.043561)
pry <- pry/sum(pry)
de3gprior_long <- de3given %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry") %>%
  arrange(pID,x)
de3gprior_long$x <- as.numeric(str_sub(de3gprior_long$x,2,10))/100
de3gprior_long$pry <- rep(pry,Ng)

utps <- de3g_fittwo %>% select(pID,beta,gamma,value)
de3gprior_long_ps <- merge(de3gprior_long,utps) 

de3gpriorpr_long <- de3gprior_long_ps %>%
  group_by(pID) %>%
  mutate(prpy = pry*(x^4)*(1-x)^1) %>%
  mutate(ppy = prpy/sum(prpy)) %>%
  mutate(pp = x^4*(1-x)^1) %>%
  mutate(py = pp/sum(pp)) %>%
  mutate(prpybest = (beta*pry+(1-beta)*rep(1/11,11))*
           (x^(gamma*4))*(1-x)^(gamma*1)) %>%
  mutate(ppyb = prpybest/sum(prpybest)) %>%
  ungroup() %>%
  select(pID,x,py,pry,ppy,ppyb,beta,gamma,value)

x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
y <- x^4*(1-x)
de3given_long$py <- rep(y/sum(y),Ng)

de3g_long <- merge(de3gpriorpr_long,de3given_long)

de3g_long_ps <- de3g_long %>%
  arrange(gamma,beta) %>%
  mutate(name = paste0("\u03b2=",round(beta,digits=2),
                       ", \u03b3=",round(gamma,digits=2),
                       "\n MSE=",round(value,digits=4),
                       " [",pID,"]"))

p <- de3g_long_ps %>%
  ggplot(mapping=aes(x=x, y=pry)) +
  #geom_line(mapping=aes(x=x,y=py),linetype="dotted",colour="darkgray") +
  geom_line(mapping=aes(x=x,y=ppy),linetype="solid",colour="darkgray") +
  geom_line(mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(colour="darkred") + 
  geom_line(mapping=aes(x=x,y=fy),colour="mediumpurple3") +
  #geom_line(mapping=aes(x=unx,y=uny),colour="dodgerblue4") +
  theme_bw() +
  facet_wrap(~name,ncol=8) +
  labs(title = "Individual fits, Gɪᴠᴇɴ: \u03b2 and \u03b3")

p

ggsave("figures/exp3_beta_gamma_indiv_fits_given_adj.png",plot=p,device="png",
       width=40,height=50, units="cm")

# look at the correlations between predicted and reported posteriors
de3gpreds <- de3gpriorpr_long %>% 
  group_by(pID) %>% 
  summarise(r = cor.test(ppy,ppyb)$estimate[[1]], 
            p = cor.test(ppy,ppyb)$p.value[[1]]) %>%
  ungroup()

de3gpreds$condition <- "Gɪᴠᴇɴ"
de3epreds$condition <- "Esᴛɪᴍᴀᴛᴇᴅ"
de3preds <- rbind(de3gpreds,de3epreds)

```

We can also get a sense of how good the fits were.

```{r goodnessfitsbetagamma, echo=FALSE, fig.height=10}
prmse <- de3_fittwo %>%
  ggplot(mapping=aes(x=value,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.005,show.legend=FALSE) + 
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "MSE (\u03b2 and \u03b3)",
       x="MSE",y="# of people")

pcorr <- de3preds %>%
  ggplot(mapping=aes(x=r,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.04,show.legend=FALSE) + 
  scale_fill_manual(values = c("mediumpurple4", "mediumpurple3")) + 
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Correlation (\u03b2 and \u03b3)",
       x="r",y="# of people")

p <- grid.arrange(prmse,pcorr,ncol=2)

p

ggsave("figures/exp3_beta_gamma_fits_adj.png",plot=p,device="png",
       width=15,height=10, units="cm")

```


# Aggregate fits

We can also look at the parameter values for the aggregate fits. First, GIVEN. 

```{r aggregatefits_given, echo=FALSE, fig.height=3}
dagg <- read.csv(file=here("datafiles/exp3all_aggregate_fits_adj.csv")) %>% as_tibble()
dagg$condition <- as.factor(dagg$condition)
levels(dagg$condition) <- c("Esᴛɪᴍᴀᴛᴇᴅ", "Gɪᴠᴇɴ")
dagg_g <- dagg %>% filter(condition=="Gɪᴠᴇɴ")
dagg_e <- dagg %>% filter(condition=="Esᴛɪᴍᴀᴛᴇᴅ")

# prediction assuming uniform prior 
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
pp <- x^4*(1-x)
py <- pp/sum(pp)

# prediction assuming the given prior
pry <- c(0.043561,0.049242,0.064394,0.104167,0.132576,0.212121,
            0.132576,0.104167,0.064394,0.049242,0.043561)
pry <- pry/sum(pry)
prpy <- pry*x^4*(1-x)
ppy <- prpy/sum(prpy)

# prediction assuming best fits
beta <- dagg_g$beta[dagg_g$fitted=="all"]
gamma <- dagg_g$gamma[dagg_g$fitted=="all"]
delta <- dagg_g$delta[dagg_g$fitted=="all"]
prpybest <- (beta*pry+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("\u03b2=",round(beta,digits=2),
  ", \u03b3=",round(gamma,digits=2)," \u03b4=",round(delta,digits=2))

pgiven_all<- de3given_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=d,mapping=aes(x=x,y=pry),colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple3") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple3") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

# prediction assuming best fits
beta <- dagg_g$beta[dagg_g$fitted=="two"]
gamma <- dagg_g$gamma[dagg_g$fitted=="two"]
delta <- dagg_g$gamma[dagg_g$fitted=="two"]
prpybest <- (beta*pry+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("Gɪᴠᴇɴ: \u03b2=",round(beta,digits=2),
  ", \u03b3=",round(gamma,digits=2))

pgiven_two <- de3given_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=d,mapping=aes(x=x,y=pry),colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple3") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple3") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

# prediction assuming best fits
beta <- dagg_g$beta[dagg_g$fitted=="beta"]
gamma <- 1
delta <- 1
prpybest <- (beta*pry+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("\u03b2=",round(beta,digits=2))

pgiven_beta <- de3given_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=d,mapping=aes(x=x,y=pry),colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple3") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple3") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

# prediction assuming best fits
gamma <- dagg_g$gamma[dagg_g$fitted=="gamma"]
beta <- 1
delta <- gamma
prpybest <- (beta*pry+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("\u03b3=",round(gamma,digits=2))

pgiven_gamma <- de3given_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=d,mapping=aes(x=x,y=pry),colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple3") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple3") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

grid.arrange(pgiven_all,pgiven_two,pgiven_beta,pgiven_gamma,ncol=4)
```

Then, ESTIMATED

```{r aggregatefits_un, echo=FALSE, fig.height=3}
# prediction assuming uniform prior 
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
pp <- x^4*(1-x)
py <- pp/sum(pp)
nr <- 4
nb <- 1

# prediction assuming their prior
prpy <- (de3eprior_lsum$mean)*x^4*(1-x)^1
ppy <- prpy/sum(prpy)

# prediction assuming best fits
beta <- dagg_e$beta[dagg_e$fitted=="all"]
gamma <- dagg_e$gamma[dagg_e$fitted=="all"]
delta <- dagg_e$delta[dagg_e$fitted=="all"]
prpybest <- (beta*(de3eprior_lsum$mean)+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("\u03b2=",round(beta,digits=2),
  ", \u03b3=",round(gamma,digits=2)," \u03b4=",round(delta,digits=2))

pest_all<- de3est_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=de3eprior_lsum,mapping=aes(x=x,y=mean),
            colour="darkred") + 
  geom_errorbar(data=de3eprior_lsum,
                mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple4") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple4") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

# prediction assuming best fits
beta <- dagg_e$beta[dagg_e$fitted=="two"]
gamma <- dagg_e$gamma[dagg_e$fitted=="two"]
delta <- dagg_e$gamma[dagg_e$fitted=="two"]
prpybest <- (beta*(de3eprior_lsum$mean)+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("Esᴛɪᴍᴀᴛᴇᴅ: \u03b2=",round(beta,digits=2),
  ", \u03b3=",round(gamma,digits=2))

pest_two <- de3est_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=de3eprior_lsum,mapping=aes(x=x,y=mean),
            colour="darkred") + 
  geom_errorbar(data=de3eprior_lsum,
                mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple4") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple4") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

# prediction assuming best fits
beta <- dagg_e$beta[dagg_e$fitted=="beta"]
gamma <- 1
delta <- 1
prpybest <- (beta*(de3eprior_lsum$mean)+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("\u03b2=",round(beta,digits=2))

pest_beta <- de3est_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=de3eprior_lsum,mapping=aes(x=x,y=mean),
            colour="darkred") + 
  geom_errorbar(data=de3eprior_lsum,
                mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple4") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple4") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

# prediction assuming best fits
gamma <- dagg_e$gamma[dagg_e$fitted=="gamma"]
delta <- gamma
beta <- 1
prpybest <- (beta*(de3eprior_lsum$mean)+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb)

t <- paste0("\u03b3=",round(gamma,digits=2))

pest_gamma <- de3est_lsum %>%
  ggplot(mapping=aes(x=x,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  geom_line(data=de3eprior_lsum,mapping=aes(x=x,y=mean),
            colour="darkred") + 
  geom_errorbar(data=de3eprior_lsum,
                mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="darkred") +
  ylim(0,1) +
  geom_line(colour="mediumpurple4") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="mediumpurple4") +
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")


grid.arrange(pest_all,pest_two,pest_beta,pest_gamma,ncol=4)

p <- grid.arrange(pest_two,pgiven_two,ncol=2)
ggsave("figures/exp3_beta_gamma_aggregate_fits_adj.png",plot=p,device="png",
       width=16,height=8, units="cm")
```
