---
title: "Creation of data files for analysis"
author: "Andrew Perfors"
output: html_document
---

This creates the data files we'll need for subsequent analyses for Experiment 2.

```{r setup, include=FALSE}
# We'll begin by loading up the libraries and data we need, as always.
knitr::opts_chunk$set(echo = TRUE)

# loading the libraries
library(tidyverse)
library(here)
library(ggplot2)
library(gridExtra)
library(rminer)

# load the full datasets
de2raw <- read.csv(file=here("Experiment2_Andy.csv")) %>% as_tibble()
# remove people who failed the bot check
bad <- de2raw %>% filter(botCheck==0 | actuallyEstimated==0)
badpeople <- bad$pID
de2 <- de2raw %>% filter(!(pID %in% badpeople))
bad <- de2raw %>% filter(pID %in% badpeople)
de2$pID <- as.factor(de2$pID)

# write the two main datasets
write.csv(bad,"datafiles/exp2_bad_data.csv")
write.csv(de2,"datafiles/exp2_good_data.csv")

# split by condition
de2peak <- de2 %>% filter(condition=="peaked")
de2unif <- de2 %>% filter(condition=="uniform")
write.csv(de2unif,"datafiles/exp2_uniform_data.csv")
write.csv(de2peak,"datafiles/exp2_peaked_data.csv")

# make the peak all nonzero
de2peak_long <- de2peak %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de2peak_long$x <- as.numeric(str_sub(de2peak_long$x,2,10))/100

de2peak_long_adj <- de2peak_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de2peak_adj <- de2peak_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de2peak_old <- de2peak %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de2peak <- merge(de2peak_old,de2peak_adj) %>%
  select(pID,condition,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,
         actuallyEstimated)

# make the uniform all nonzero
de2unif_long <- de2unif %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de2unif_long$x <- as.numeric(str_sub(de2unif_long$x,2,10))/100

de2unif_long_adj <- de2unif_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de2unif_adj <- de2unif_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de2unif_old <- de2unif %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de2unif <- merge(de2unif_old,de2unif_adj) %>%
  select(pID,condition,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,
         actuallyEstimated)

de2 <- rbind(de2peak,de2unif)
write.csv(de2,"datafiles/exp2_good_data_adj.csv")

```


## Peaked prior

This contains the code to fit individuals in three different ways. 

1. Fit $\beta$, $\gamma$, and $\delta$. Output is in `exp2_peaked_allfits_adj.csv`

2. Fit beta and one variable ($\gamma$) which is the same for $\gamma$ and $\delta$, i.e., it enforces them to be the same. Output is in `exp2_peaked_twofits_adj.csv`

3. Fit only $\beta$, and force $\gamma=\delta=1$. The point of this is to see if the fits we get on $\beta$ which imply they are ignoring the prior are an artefact of also fitting $\delta$ and $\gamma$. Output is in `exp2_peaked_betafits_adj.csv`

4. Fit only $\gamma$, and assume that $\beta=1$. The point of this is the opposite of #3. Output is in `exp2_peaked_gammafits_adj.csv`

```{r fitthingspeaked}
de2peak_long <- de2peak %>% 
  select(-c(condition,age,gender,botCheck,actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="y")
de2peak_long$x <- as.numeric(str_sub(de2peak_long$x,2,10))/100

# the function that fits beta, gamma, and delta
frpeakall <- function(ps,d) {
   pry <- c(0,0,0,0,0,0.08,0.08,0.2,0.6,0.04,0)
   uny <- rep(1/11,11)
   x <- d$x
   y <- d$y
   beta <- ps[1]
   gamma <- ps[2]
   delta <- ps[3]
   y <- y/sum(y)
   likelihood <- x^(gamma*4)*(1-x)^(delta*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits beta and gamma/delta as one
frpeaktwo <- function(ps,d) {
   pry <- c(0,0,0,0,0,0.08,0.08,0.2,0.6,0.04,0)
   uny <- rep(1/11,11)
   x <- d$x
   y <- d$y
   beta <- ps[1]
   gamma <- ps[2]
   y <- y/sum(y)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only beta
frpeakbeta <- function(ps,d) {
   pry <- c(0,0,0,0,0,0.08,0.08,0.2,0.6,0.04,0)
   uny <- rep(1/11,11)
   x <- d$x
   y <- d$y
   beta <- ps[1]
   gamma <- 1
   y <- y/sum(y)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only gamma
frpeakgamma <- function(ps,d) {
   pry <- c(0,0,0,0,0,0.08,0.08,0.2,0.6,0.04,0)
   x <- d$x
   y <- d$y
   gamma <- ps[1]
   y <- y/sum(y)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- pry
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# fitting delta, gamma, and beta
ddpeakall <- de2peak_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1,1),frpeakall,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001,0.0000001),
                          upper=c(0.9999999,50,50))))

de2peak_all <- de2peak
de2peak_all$beta <- NA
de2peak_all$gamma <- NA
de2peak_all$delta <- NA
de2peak_all$value <- NA

for (i in 1:nrow(de2peak_all)) {
   pid <- ddpeakall$pID[i]
   de2peak_all$beta[de2peak_all$pID==pid] <-
    ddpeakall$fit[[i]]$par[1]
   de2peak_all$gamma[de2peak_all$pID==pid] <-
    ddpeakall$fit[[i]]$par[2]
   de2peak_all$delta[de2peak_all$pID==pid] <-
    ddpeakall$fit[[i]]$par[3]
   de2peak_all$value[de2peak_all$pID==pid] <-
    ddpeakall$fit[[i]]$value[1]
}

write.csv(de2peak_all,"datafiles/exp2_peaked_allfits_adj.csv")

# fitting delta/gamma, and beta
ddpeaktwo <- de2peak_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),frpeaktwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

de2peak_two <- de2peak
de2peak_two$beta <- NA
de2peak_two$gamma <- NA
de2peak_two$value <- NA

for (i in 1:nrow(de2peak_two)) {
      pid <- ddpeaktwo$pID[i]
   de2peak_two$beta[de2peak_two$pID==pid] <-
    ddpeaktwo$fit[[i]]$par[1]
   de2peak_two$gamma[de2peak_two$pID==pid] <-
    ddpeaktwo$fit[[i]]$par[2]
   de2peak_two$value[de2peak_two$pID==pid] <-
    ddpeaktwo$fit[[i]]$value[1]
}

write.csv(de2peak_two,"datafiles/exp2_peaked_twofits_adj.csv")

# fitting only beta
ddpeakbeta <- de2peak_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5),frpeakbeta,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(0.9999999))))

de2peak_beta <- de2peak
de2peak_beta$beta <- NA
de2peak_beta$value <- NA

for (i in 1:nrow(de2peak_beta)) {
   pid <- ddpeakbeta$pID[i]
   de2peak_beta$beta[de2peak_beta$pID==pid] <-
    ddpeakbeta$fit[[i]]$par[1]
   de2peak_beta$value[de2peak_beta$pID==pid] <-
    ddpeakbeta$fit[[i]]$value[1]
}

write.csv(de2peak_beta,"datafiles/exp2_peaked_betafits_adj.csv")

# fitting only gamma
ddpeakgamma <- de2peak_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1),frpeakgamma,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(50))))

de2peak_gamma <- de2peak
de2peak_gamma$beta <- NA
de2peak_gamma$value <- NA

for (i in 1:nrow(de2peak_gamma)) {
   pid <- ddpeakbeta$pID[i]
   de2peak_gamma$gamma[de2peak_gamma$pID==pid] <-
    ddpeakgamma$fit[[i]]$par[1]
   de2peak_gamma$value[de2peak_gamma$pID==pid] <-
    ddpeakgamma$fit[[i]]$value[1]
}

write.csv(de2peak_gamma,"datafiles/exp2_peaked_gammafits_adj.csv")
```

## Uniform prior

Now we're going to do the same thing with the uniform condition. Here the prior is actually uniform so fitting $\beta$ doesn't make sense. So we have only two things.

1. Fit $\gamma$ and $\delta$. Output is in `exp2_uniform_allfits_adj.csv`

2. Fit one variable ($\gamma$) which is the same for $\gamma$ and $\delta$, i.e., it enforces them to be the same. Output is in `exp2_uniform_twofits_adj.csv`


```{r fitthingsuniform}
de2unif_long <- de2unif %>% 
  select(-c(condition,age,gender,botCheck,actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="y")
de2unif_long$x <- as.numeric(str_sub(de2unif_long$x,2,10))/100

# the function that fits gamma and delta
frunifall <- function(ps,d) {
   x <- d$x
   y <- d$y
   gamma <- ps[1]
   delta <- ps[2]
   y <- y/sum(y)
   likelihood <- x^(gamma*4)*(1-x)^(delta*1)
   prior <- rep(1/11,11)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}


# the function that fits gamma/delta as one
fruniftwo <- function(ps,d) {
   x <- d$x
   y <- d$y
   gamma <- ps[1]
   y <- y/sum(y)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- rep(1/11,11)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# fitting delta and gamma
ddunifall <- de2unif_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1,1),frunifall,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(50,50))))

de2unif_all <- de2unif
de2unif_all$gamma <- NA
de2unif_all$delta <- NA
de2unif_all$value <- NA

for (i in 1:nrow(de2unif_all)) {
   pid <- ddunifall$pID[i]
   de2unif_all$gamma[de2unif_all$pID==pid] <-
    ddunifall$fit[[i]]$par[1]
   de2unif_all$delta[de2unif_all$pID==pid] <-
    ddunifall$fit[[i]]$par[2]
   de2unif_all$value[de2unif_all$pID==pid] <-
    ddunifall$fit[[i]]$value[1]
}

write.csv(de2unif_all,"datafiles/exp2_uniform_allfits_adj.csv")

# fitting delta/gamma
dduniftwo <- de2unif_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1),fruniftwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(50))))

de2unif_two <- de2unif
de2unif_two$gamma <- NA
de2unif_two$value <- NA

for (i in 1:nrow(de2unif_two)) {
   pid <- dduniftwo$pID[i]
   de2unif_two$gamma[de2unif_two$pID==pid] <-
    dduniftwo$fit[[i]]$par[1]
   de2unif_two$value[de2unif_two$pID==pid] <-
    dduniftwo$fit[[i]]$value[1]
}

write.csv(de2unif_two,"datafiles/exp2_uniform_twofits_adj.csv")
```



## Calculate aggregate best-fit parameters

This contains the code for the aggregate best fits in different ways. First we'll do it just for the peaked condition. There are three things:

1. Fit $\beta$, $\gamma$, and $\delta$. Output is in `exp2agg_peaked_allfits_adj.csv`

2. Fit $\beta$ and one variable ($\gamma$) which is the same for $\gamma$ and $\delta$, i.e., it enforces them to be the same. Output is in `exp2agg_peaked_twofits_adj.csv`

3. Fit only $\beta$, and force $\gamma=\delta=1$. The point of this is to see if the fits we get on $\beta$ which imply they are ignoring the prior are an artefact of also fitting $\delta$ and $\gamma$. Output is in `exp2agg_peaked_betafits_adj.csv`

4. Fit only $\gamma$, and force $\beta=1$.

```{r fitthingsaggregatepeaked}
# make dataset with aggregate results
de2_long <- de2 %>% 
  select(-c(age,gender,botCheck,actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="y")
de2_long$x <- as.numeric(str_sub(de2_long$x,2,10))/100

de2_lsum <- de2_long %>%
  group_by(condition,x) %>%
  summarise(y=mean(y)) %>%
  ungroup()
write.csv(de2_lsum,"datafiles/exp2all_aggregate_curves_adj.csv")

de2peak_lsum <- de2_lsum %>% filter(condition=="peaked")
de2unif_lsum <- de2_lsum %>% filter(condition=="uniform")

# fitting delta, gamma, and beta on peaked
ddaggall_pk <- optim(c(0.5,1,1),frpeakall,d=de2peak_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001,0.0000001),
                  upper=c(0.9999999,50,50))

# fitting gamma and beta on peaked
ddaggtwo_pk <- optim(c(0.5,1),frpeaktwo,d=de2peak_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001),
                  upper=c(0.9999999,50))

# fitting beta on peaked
ddaggbeta_pk <- optim(c(0.5),frpeakbeta,d=de2peak_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(0.9999999))

# fitting gamma on peaked
ddagggamma_pk <- optim(c(1),frpeakgamma,d=de2peak_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(50))

# fitting delta and gamma on uniform
ddaggall_un <- optim(c(1,1),frunifall,d=de2unif_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001),
                  upper=c(50,50))

# fitting gamma on uniform
ddaggtwo_un <- optim(c(1,1),fruniftwo,d=de2unif_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),
                  upper=c(50))

condition <- c(rep("peaked",4),rep("uniform",2))
fitted <- c("all","two","beta","gamma","all","two")
beta <- c(ddaggall_pk$par[1],ddaggtwo_pk$par[1],ddaggbeta_pk$par[1],
          NA,NA,NA)
gamma <- c(ddaggall_pk$par[2],ddaggtwo_pk$par[2],NA,ddagggamma_pk$par[1],
          ddaggall_un$par[1],ddaggtwo_un$par[1])
delta <- c(ddaggall_pk$par[3],NA,NA,NA,ddaggall_un$par[2],NA)
value <- c(ddaggall_pk$value,ddaggtwo_pk$value,ddaggbeta_pk$value,
           ddagggamma_pk$value,ddaggall_un$value,ddaggtwo_un$value)
dagg <- tibble(condition,fitted,beta,gamma,delta,value)
write.csv(dagg,"datafiles/exp2all_aggregate_fits_adj.csv")
```