---
title: "Analyses of main data: Experiment 2"
author: "Andrew Perfors"
output: html_document
---

This is exactly the same as the others but we're going to limit ourselves only to the people in Experiment 2 who we could fit well, just to see if our results are robust to that. If they change dramatically that indicates that they are being shaped by people we can't fit anyway.


```{r setup, include=FALSE}
# We'll begin by loading up the libraries and data we need, as always.
knitr::opts_chunk$set(echo = TRUE)

# loading the libraries
library(tidyverse)
library(here)
library(ggplot2)
library(gridExtra)
library(plotly)

# load the full datasets
de2 <- read.csv(file=here("datafiles/exp2_good_data.csv")) %>% as_tibble()
de2$pID <- as.factor(de2$pID)
de2$condition <- as.factor(de2$condition)
levels(de2$condition) <- c("Pᴇᴀᴋᴇᴅ", "Uɴɪғᴏʀᴍ")

# load the fitted data
de2p_fitall <- read.csv(file=here("datafiles/exp2_peaked_allfits_adj.csv")) %>%
  as_tibble()
de2p_fittwo <- read.csv(file=here("datafiles/exp2_peaked_twofits_adj.csv")) %>%
  as_tibble()
de2p_fitbeta <- read.csv(file=here("datafiles/exp2_peaked_betafits_adj.csv")) %>%
  as_tibble()
de2p_fitgamma <- read.csv(file=here("datafiles/exp2_peaked_gammafits_adj.csv")) %>%
  as_tibble()
de2u_fitall <- read.csv(file=here("datafiles/exp2_uniform_allfits_adj.csv")) %>%
  as_tibble()
de2u_fittwo <- read.csv(file=here("datafiles/exp2_uniform_twofits_adj.csv")) %>%
  as_tibble()

# convert "value" to mean squared error
de2p_fitall$value <- de2p_fitall$value/11
de2p_fitbeta$value <- de2p_fitbeta$value/11
de2p_fittwo$value <- de2p_fittwo$value/11
de2p_fitgamma$value <- de2p_fitgamma$value/11
de2u_fitall$value <- de2u_fitall$value/11
de2u_fittwo$value <- de2u_fittwo$value/11

# rename
de2p_fitall$condition <- as.factor(de2p_fitall$condition)
levels(de2p_fitall$condition) <- c("Pᴇᴀᴋᴇᴅ")
de2p_fitbeta$condition <- as.factor(de2p_fitbeta$condition)
levels(de2p_fitbeta$condition) <- c("Pᴇᴀᴋᴇᴅ")
de2p_fittwo$condition <- as.factor(de2p_fittwo$condition)
levels(de2p_fittwo$condition) <- c("Pᴇᴀᴋᴇᴅ")
de2p_fitgamma$condition <- as.factor(de2p_fitgamma$condition)
levels(de2p_fitgamma$condition) <- c("Pᴇᴀᴋᴇᴅ")

de2u_fitall$condition <- as.factor(de2u_fitall$condition)
levels(de2u_fitall$condition) <- c("Uɴɪғᴏʀᴍ")
de2u_fittwo$condition <- as.factor(de2u_fittwo$condition)
levels(de2u_fittwo$condition) <- c("Uɴɪғᴏʀᴍ")

# remove people
thresholdval <- 0.01
badpeak <- de2p_fittwo$pID[de2p_fittwo$value>thresholdval]
badun <- de2u_fittwo$pID[de2u_fittwo$value>thresholdval]
badfits <- unique(c(badpeak,badun))

de2_bad <- de2 %>% filter((pID %in% badfits))
de2p_fitall_bad <- de2p_fitall %>% filter((pID %in% badfits))
de2p_fittwo_bad <- de2p_fittwo %>% filter((pID %in% badfits))
de2p_fitbeta_bad <- de2p_fitbeta %>% filter((pID %in% badfits))
de2p_fitgamma_bad <- de2p_fitgamma %>% filter((pID %in% badfits))
de2u_fitall_bad <- de2u_fitall %>% filter((pID %in% badfits))
de2u_fittwo_bad <- de2u_fittwo %>% filter((pID %in% badfits))

de2 <- de2 %>% filter(!(pID %in% badfits))
de2p_fitall <- de2p_fitall %>% filter(!(pID %in% badfits))
de2p_fittwo <- de2p_fittwo %>% filter(!(pID %in% badfits))
de2p_fitbeta <- de2p_fitbeta %>% filter(!(pID %in% badfits))
de2p_fitgamma <- de2p_fitgamma %>% filter(!(pID %in% badfits))
de2u_fitall <- de2u_fitall %>% filter(!(pID %in% badfits))
de2u_fittwo <- de2u_fittwo %>% filter(!(pID %in% badfits))

de2peak <- de2 %>% filter(condition=="Pᴇᴀᴋᴇᴅ")
de2unif <- de2 %>% filter(condition=="Uɴɪғᴏʀᴍ")
de2peak_bad <- de2_bad %>% filter(condition=="Pᴇᴀᴋᴇᴅ")
de2unif_bad <- de2_bad %>% filter(condition=="Uɴɪғᴏʀᴍ")

# combine files
de2u_fitall$beta <- NA
de2_fitall <- rbind(de2p_fitall,de2u_fitall)
de2u_fittwo$beta <- NA
de2_fittwo <- rbind(de2p_fittwo,de2u_fittwo)

N <- length(unique(de2$pID))
Np <- length(unique(de2peak$pID))
Nu <- length(unique(de2unif$pID))
badN <- length(unique(de2_bad$pID))
badNp <- length(badpeak)
badNu <- length(badun)
```

## Let's get rid of people

I'm going to arbitrarily decide to get rid of the people whose fit in the (beta,gamma) case is worse than `r thresholdval` for either of the conditions. This removes `r length(badfits)` out of 239 people.

## Basic performance

First let's have a look at the **peaked** and **uniform** conditions, which had different priors but each saw four red and one blue. 

```{r exp2_posteriors, echo=FALSE,fig.height=3, fig.width=8}
# make longer form
de2peak_long <- de2peak %>% 
  select(-c(condition,age,gender,botCheck,actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="px",values_to="py")
de2peak_long$px <- as.numeric(str_sub(de2peak_long$px,2,10))/100

de2peak_long_bad <- de2peak_bad %>% 
  select(-c(condition,age,gender,botCheck,actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="px",values_to="py")
de2peak_long_bad$px <- as.numeric(str_sub(de2peak_long_bad$px,2,10))/100

# make summary dataset for graphing
de2peak_lsum <- de2peak_long %>%
  group_by(px) %>%
  summarise(mean=mean(py),
            sd=sd(py),
            n=n(),
            sderr = sd/sqrt(n)) %>%
  ungroup()

peakpost <- de2peak_lsum %>%
  ggplot(mapping=aes(x=px,y=mean)) +
  geom_jitter(data=de2peak_long,mapping=aes(x=px,y=py),
              alpha=0.1,colour="darkgreen") +
  geom_line(colour="darkgreen") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="darkgreen") +
  theme_bw() +
  labs(title = "Pᴇᴀᴋᴇᴅ",x="Proportion of red",y="Probability")

# make longer form
de2unif_long <- de2unif %>% 
  select(-c(condition,age,gender,botCheck,actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="ux",values_to="uy")
de2unif_long$ux <- as.numeric(str_sub(de2unif_long$ux,2,10))/100

de2unif_long_bad <- de2unif_bad %>% 
  select(-c(condition,age,gender,botCheck,actuallyEstimated)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="ux",values_to="uy")
de2unif_long_bad$ux <- as.numeric(str_sub(de2unif_long_bad$ux,2,10))/100

# make summary dataset for graphing
de2unif_lsum <- de2unif_long %>%
  group_by(ux) %>%
  summarise(mean=mean(uy),
            sd=sd(uy),
            n=n(),
            sderr = sd/sqrt(n)) %>%
  ungroup()

unifpost <- de2unif_lsum %>%
  ggplot(mapping=aes(x=ux,y=mean)) +
  geom_jitter(data=de2unif_long,mapping=aes(x=ux,y=uy),
              alpha=0.1,colour="green3") +
  geom_line(colour="green3") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="green3") +
  theme_bw() +
  labs(title = "Uɴɪғᴏʀᴍ",x="Proportion of red",y="Probability")

p <- grid.arrange(peakpost,unifpost,ncol=2)
ggsave("figures/exp2_good_posteriors_peak_unif_adj.png",plot=p,device="png",
       width=16,height=6, units="cm")

```

# FITS

### Looking at fitted values: $\beta$, $\delta$, and $\gamma$

Let's have a look at the distribution of parameters. As a reminder:

$\beta$: determines to what degree participants use their stated prior, and to what degree they use the uniform distribution to deduce their posterior. If $\beta=1$ that means it's all prior, if $\beta=0$ it is all uniform distribution

$\gamma$: how much they weighted the red chips they saw. if $\gamma=1$ it is veridical, lower is underweighting, higher is overweighting. 

$\delta$: how much they weighted the blue chips they saw. if $\delta=1$ it is veridical, lower is underweighting, higher is overweighting. 

Note that there is no $\beta$ parameter in the uniform condition, since the given prior is already uniform. So all the things with three parameters don't include it.

```{r viewdatascatall, echo=FALSE, fig.height=6, fig.width=4}
psbg <- de2p_fitall %>%
  ggplot(mapping=aes(x=beta,y=gamma,colour=delta)) +
  geom_point(alpha=0.7,size=2) + 
  theme_bw() +
  labs(title = "\u03b2 vs \u03b3",x="\u03b2",y="\u03b3")

psbd <- de2p_fitall %>%
  ggplot(mapping=aes(x=beta,y=delta,colour=gamma)) +
  geom_point(alpha=0.7,size=2) + 
  theme_bw() +
  labs(title = "\u03b2 vs \u03b4",x="\u03b2",y="\u03b4")

psgd <- de2p_fitall %>%
  ggplot(mapping=aes(x=gamma,y=delta,colour=beta)) +
  geom_point(alpha=0.7,size=2) + 
  theme_bw() +
  labs(title = "\u03b3 vs \u03b4",x="\u03b3",y="\u03b4")

grid.arrange(psbg,psbd,psgd,nrow=3)
```

And also a 3D plot

```{r viewdata3dall, echo=FALSE, fig.height=4, fig.width=4}
p <- plot_ly(x=de2p_fitall$beta, y=de2p_fitall$gamma, z=de2p_fitall$delta,
             type="scatter3d",mode="markers", color=de2p_fitall$beta)
p <- layout(p, scene = list(xaxis = list(title="\u03b2"),
                            yaxis = list(title = "\u03b3"),
                            zaxis = list(title="\u03b4")))
p
```

Finally, let's look at histograms of all of the variables.

```{r histallfits, echo=FALSE, fig.height=6, fig.width=4}
pb <- de2_fitall %>%
  ggplot(mapping=aes(x=beta,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.1,show.legend=FALSE) + 
  scale_fill_manual(values = c("darkgreen", "green3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b2",x="\u03b2",y="# of people")

pg <- de2_fitall %>%
  ggplot(mapping=aes(x=log(gamma),fill=condition)) +
    geom_histogram(alpha=0.7,colour="black",binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  scale_fill_manual(values = c("darkgreen", "green3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b3",x="log(\u03b3)",y="# of people")

pd <- de2_fitall %>%
  ggplot(mapping=aes(x=log(delta),fill=condition)) +
    geom_histogram(alpha=0.7,colour="black",binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  scale_fill_manual(values = c("darkgreen", "green3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b4",x="log(\u03b4)",y="# of people")

p <- grid.arrange(pb,pg,pd,ncol=3)
ggsave("figures/exp2_beta_gamma_delta_histograms_adj.png",
       plot=p,device="png",
       width=24,height=10, units="cm")
```

### Looking at fitted values: $\beta$ alone

I wanted to see if the beta values would be different if we weren't also fitting $\delta$ and $\gamma$. So let's look at that histogram.

```{r histbetafits, echo=FALSE, fig.height=3, fig.width=4}
pbeta <- de2p_fitbeta %>%
  ggplot(mapping=aes(x=beta)) +
  geom_histogram(alpha=0.7,fill="darkgreen",colour="black",binwidth=0.1) + 
  theme_bw() +
  labs(title = "Distribution of \u03b2",x="\u03b2",y="# of people")

pbeta
ggsave("figures/exp2_good_beta_histograms_adj.png",plot=pbeta,device="png",
       width=8,height=5, units="cm")

# percent less than 0.1
pl1p <- round(100*sum(de2p_fitbeta$beta<0.1)/Np,1)
# percent greater than 0.9
pg1p <- round(100*sum(de2p_fitbeta$beta>0.9)/Np,1)
```

For the priors: `r pl1p`% had $\beta$ less than 0.1, and `r pg1p`% had $\beta$ greater than 0.9. 

### Looking at fitted values: $\gamma$ alone

I wanted to see if the $\gamma$ values would be different if we weren't also fitting $\beta$ and $\delta$. So let's look at that histogram.

```{r histgammafits, echo=FALSE, fig.height=3, fig.width=4}
pgamma <- de2p_fitgamma %>%
  ggplot(mapping=aes(x=log(gamma))) +
    geom_histogram(alpha=0.7,colour="black",fill="darkgreen",
                   binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  theme_bw() +
  labs(title = "Distribution of \u03b3 only",x="log(\u03b3)",y="# of people")

pgamma
ggsave("figures/exp2_good_gamma_histograms_adj.png",plot=pgamma,device="png",
       width=8,height=5, units="cm")

p <- grid.arrange(pbeta,pgamma,ncol=2)
ggsave("figures/exp2_good_combined_histograms_adj.png",plot=p,device="png",
       width=16,height=5, units="cm")

# percent less than 0.1
pl1p <- round(100*sum(de2p_fitgamma$gamma<1)/Np,1)
```

For the likelihoods: `r pl1p`% in PEAKED had $\gamma$ less than 1 (no need to run UNIFORM, as that would be the same as the $\gamma$ distribution below).


### Looking at fitted values: $\beta$ and $\gamma$ alone

Here we assume one parameter (call it $\gamma$) instead of two separate ones ($\gamma$ and $\delta$). i.e. this forces them to be the same and can be thought of as a conservatism parameter. I wanted to look at this because I think it might be a lot more interpretable than having both.

$\beta$: determines to what degree participants use their stated prior, and to what degree they use the uniform distribution to deduce their posterior. If $\beta=1$ that means it's all prior, if $\beta=0$ it is all uniform distribution

$\gamma$: how much they weighted the chips they saw. if $\gamma=1$ it is veridical, lower is underweighting, higher is overweighting. 

```{r viewdatascattwo, echo=FALSE, fig.height=3, fig.width=4}
p <- de2p_fittwo %>%
  ggplot(mapping=aes(x=beta,y=log(gamma))) +
  geom_point(alpha=0.6,size=3,colour="darkgreen") + 
  theme_bw() +
  labs(title = "\u03b2 vs \u03b3",x="\u03b2",y="log(\u03b3)")

p
ggsave("figures/exp2_good_beta_gamma_fitted_values_adj.png",plot=p,device="png",
       width=16,height=6, units="cm")
```

Let's calculate the Spearman correlation:

```{r correlationbetagamma}
cor.test(de2p_fittwo$beta,de2p_fittwo$gamma,method="spearman")
```

And a histogram of them too

```{r histtwofits, echo=FALSE, fig.height=4, fig.width=8}
pb <- de2_fittwo %>%
  ggplot(mapping=aes(x=beta,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.1,show.legend=FALSE) + 
  scale_fill_manual(values = c("darkgreen", "green3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b2",x="\u03b2",y="# of people")

pg <- de2_fittwo %>%
  ggplot(mapping=aes(x=log(gamma),fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=1,show.legend=FALSE) + 
  geom_vline(xintercept = 0, linetype="dotted", color = "black") +
  scale_fill_manual(values = c("darkgreen", "green3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Distribution of \u03b3",x="log(\u03b3)",y="# of people")

p <- grid.arrange(pb,pg,ncol=2)
ggsave("figures/exp2_good_beta_gamma_histograms_adj.png",plot=p,device="png",
       width=16,height=10, units="cm")

# percent less than 0.1
pl1p <- round(100*sum(de2p_fittwo$beta<0.1)/Np,1)
# percent greater than 0.9
pg1p <- round(100*sum(de2p_fittwo$beta>0.9)/Np,1)

# likelihood percent less than 1
pll1f <- round(100*sum(de2p_fittwo$gamma<1)/Np,1)
pll1u <- round(100*sum(de2u_fittwo$gamma<1)/Nu,1)

```

For the priors: `r pl1p`% had $\beta$ less than 0.1, and `r pg1p`% had $\beta$ greater than 0.9. 

For the likelihoods: `r pll1f`% in PEAKED and `r pll1u`% in UNIFORM had $\gamma$ less than 1 (i.e., were conservative).


# Individuals: Peaked prior

So now let's look at individuals - look at their posterior, based on the best-fit beta and gamma. 

*red line*: the given prior

*dark green line*: their reported posterior

*dotted grey*: Bayes rule prediction assuming uniform prior (not shown)

*solid grey*: Bayes rule prediction assuming the given prior

*dotted black*: line based on best-fit beta and gamma

```{r individual_people_betagamma, echo=FALSE, fig.height=40}
# first the bad fits
pry <- c(0,0,0,0,0,0.08,0.08,0.2,0.6,0.04,0)
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
de2peak_long_bad$pry <- rep(pry,nrow(de2peak_long_bad)/11)

ptps <- de2p_fittwo_bad %>% select(pID,beta,gamma,value)
de2peak_fittwo_bad <- merge(de2peak_long_bad,ptps) 

de2peak_fittwo_sum_bad <- de2peak_fittwo_bad %>%
  group_by(pID) %>%
  mutate(prpy = pry*(px^4)*(1-px)) %>%
  mutate(ppy = prpy/sum(prpy)) %>%
  mutate(prpybest = (beta*pry+(1-beta)*rep(1/11,11))*
           (px^(gamma*4))*(1-x)^gamma) %>%
  mutate(ppyb = prpybest/sum(prpybest)) %>%
  mutate(ply = px^4*(1-px)) %>%
  mutate(ly = ply/sum(ply)) %>%
  ungroup() %>%
  select(pID,px,py,pry,ly,ppy,ppyb,beta,gamma,value) %>%
  mutate(name = paste0("\u03b2=",round(beta,digits=2),
                       ", \u03b3=",round(gamma,digits=2),
                       "\n MSE=",round(value,digits=4),
                       " [",pID,"]"))

p <- de2peak_fittwo_sum_bad %>%
  ggplot(mapping=aes(x=px, y=pry)) +
  #geom_line(mapping=aes(x=px,y=ly),linetype="dotted",colour="darkgray") +
  geom_line(mapping=aes(x=px,y=ppy),linetype="solid",colour="darkgray") +
  geom_line(mapping=aes(x=px,y=ppyb),linetype="dotted",
           colour="black") +
  geom_line(colour="darkred") + 
  #geom_line(mapping=aes(x=x,y=fy),colour="green3") +
  geom_line(mapping=aes(x=px,y=py),colour="darkgreen") +
  theme_bw() +
  facet_wrap(~name,ncol=8) +
  labs(title = "Individual fits, Pᴇᴀᴋᴇᴅ: \u03b2 and \u03b3")

ggsave("figures/exp2_bad_beta_gamma_indiv_fits_peaked_adj.png",plot=p,device="png",
       width=40,height=14, units="cm")

# then the good fits
pry <- c(0,0,0,0,0,0.08,0.08,0.2,0.6,0.04,0)
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
de2peak_long$pry <- rep(pry,nrow(de2peak_long)/11)

ptps <- de2p_fittwo %>% select(pID,beta,gamma,value)
de2peak_fittwo <- merge(de2peak_long,ptps) 

de2peak_fittwo_sum <- de2peak_fittwo %>%
  group_by(pID) %>%
  mutate(prpy = pry*(px^4)*(1-px)) %>%
  mutate(ppy = prpy/sum(prpy)) %>%
  mutate(prpybest = (beta*pry+(1-beta)*rep(1/11,11))*
           (px^(gamma*4))*(1-x)^gamma) %>%
  mutate(ppyb = prpybest/sum(prpybest)) %>%
  mutate(ply = px^4*(1-px)) %>%
  mutate(ly = ply/sum(ply)) %>%
  ungroup() %>%
  select(pID,px,py,pry,ly,ppy,ppyb,beta,gamma,value) %>%
  mutate(name = paste0("\u03b2=",round(beta,digits=2),
                       ", \u03b3=",round(gamma,digits=2),
                       "\n MSE=",round(value,digits=4),
                       " [",pID,"]"))

p <- de2peak_fittwo_sum %>%
  ggplot(mapping=aes(x=px, y=pry)) +
  #geom_line(mapping=aes(x=px,y=ly),linetype="dotted",colour="darkgray") +
  geom_line(mapping=aes(x=px,y=ppy),linetype="solid",colour="darkgray") +
  geom_line(mapping=aes(x=px,y=ppyb),linetype="dotted",
           colour="black") +
  geom_line(colour="darkred") + 
  #geom_line(mapping=aes(x=x,y=fy),colour="green3") +
  geom_line(mapping=aes(x=px,y=py),colour="darkgreen") +
  theme_bw() +
  facet_wrap(~name,ncol=8) +
  labs(title = "Individual fits, Pᴇᴀᴋᴇᴅ: \u03b2 and \u03b3")

ggsave("figures/exp2_good_beta_gamma_indiv_fits_peaked_adj.png",plot=p,device="png",
       width=40,height=50, units="cm")

# look at the correlations between predicted and reported posteriors
de2predspeak <- de2peak_fittwo_sum %>% 
  group_by(pID) %>% 
  summarise(r = cor.test(ppy,ppyb)$estimate[[1]], 
            p = cor.test(ppy,ppyb)$p.value[[1]]) %>%
  ungroup()
```

# Individuals: Uniform prior

So now let's look at individuals - look at their posterior, based on the best-fit beta and gamma. 

*red line*: the given prior

*light green line*: their reported posterior

*solid grey*: Bayes rule prediction assuming uniform prior

*dotted black*: line based on best-fit beta and gamma

```{r individual_people_betagamma_unif, echo=FALSE, fig.height=40}
# first the bad fits
pry <- rep(1/11,11)
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
de2unif_long_bad$pry <- rep(pry,nrow(de2unif_long_bad)/11)

utps <- de2u_fittwo_bad %>% select(pID,gamma,value)
de2unif_fittwo_bad <- merge(de2unif_long_bad,utps) 

de2unif_fittwo_sum_bad <- de2unif_fittwo_bad %>%
  group_by(pID) %>%
  mutate(prpy = pry*(ux^4)*(1-ux)) %>%
  mutate(ppy = prpy/sum(prpy)) %>%
  mutate(prpybest = pry*(ux^(gamma*4))*(1-ux)^gamma) %>%
  mutate(ppyb = prpybest/sum(prpybest)) %>%
  mutate(ply = ux^4*(1-ux)) %>%
  mutate(ly = ply/sum(ply)) %>%
  ungroup() %>%
  select(pID,ux,uy,pry,ly,ppy,ppyb,gamma,value) %>%
    mutate(name = paste0("\u03b3=",round(gamma,digits=2),
                       "\n MSE=",round(value,digits=4),
                       " [",pID,"]"))

p <- de2unif_fittwo_sum_bad %>%
  ggplot(mapping=aes(x=ux, y=pry)) +
  #geom_line(mapping=aes(x=ux,y=ly),linetype="dotted",colour="darkgray") +
  geom_line(mapping=aes(x=ux,y=ppy),linetype="solid",colour="darkgray") +
  geom_line(mapping=aes(x=ux,y=ppyb),linetype="dotted",
           colour="black") +
  geom_line(colour="darkred") + 
  geom_line(mapping=aes(x=ux,y=uy),colour="green3") +
  theme_bw() +
  facet_wrap(~name,ncol=8) +
  labs(title = "Individual fits, Uɴɪғᴏʀᴍ: \u03b2 and \u03b3")

ggsave("figures/exp2_bad_beta_gamma_indiv_fits_uniform_adj.png",plot=p,device="png",
       width=40,height=24, units="cm")

# then the good fits
pry <- rep(1/11,11)
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
de2unif_long$pry <- rep(pry,nrow(de2unif_long)/11)

utps <- de2u_fittwo %>% select(pID,gamma,value)
de2unif_fittwo <- merge(de2unif_long,utps) 

de2unif_fittwo_sum <- de2unif_fittwo %>%
  group_by(pID) %>%
  mutate(prpy = pry*(ux^4)*(1-ux)) %>%
  mutate(ppy = prpy/sum(prpy)) %>%
  mutate(prpybest = pry*(ux^(gamma*4))*(1-ux)^gamma) %>%
  mutate(ppyb = prpybest/sum(prpybest)) %>%
  mutate(ply = ux^4*(1-ux)) %>%
  mutate(ly = ply/sum(ply)) %>%
  ungroup() %>%
  select(pID,ux,uy,pry,ly,ppy,ppyb,gamma,value) %>%
    mutate(name = paste0("\u03b3=",round(gamma,digits=2),
                       "\n MSE=",round(value,digits=4),
                       " [",pID,"]"))

p <- de2unif_fittwo_sum %>%
  ggplot(mapping=aes(x=ux, y=pry)) +
  #geom_line(mapping=aes(x=ux,y=ly),linetype="dotted",colour="darkgray") +
  geom_line(mapping=aes(x=ux,y=ppy),linetype="solid",colour="darkgray") +
  geom_line(mapping=aes(x=ux,y=ppyb),linetype="dotted",
           colour="black") +
  geom_line(colour="darkred") + 
  geom_line(mapping=aes(x=ux,y=uy),colour="green3") +
  theme_bw() +
  facet_wrap(~name,ncol=8) +
  labs(title = "Individual fits, Uɴɪғᴏʀᴍ: \u03b2 and \u03b3")

ggsave("figures/exp2_good_beta_gamma_indiv_fits_uniform_adj.png",plot=p,device="png",
       width=40,height=50, units="cm")

# look at the correlations between predicted and reported posteriors
de2predsunif <- de2unif_fittwo_sum  %>% 
  group_by(pID) %>% 
  summarise(r = cor.test(ppy,ppyb)$estimate[[1]], 
            p = cor.test(ppy,ppyb)$p.value[[1]]) %>%
  ungroup()

de2predspeak$condition <- "peaked"
de2predsunif$condition <- "uniform"
de2preds <- rbind(de2predspeak,de2predsunif)
```

We can also get a sense of how good the fits were.

```{r goodnessfitsbetagamma, echo=FALSE, fig.height=10}
prmse <- de2_fittwo %>%
  ggplot(mapping=aes(x=value,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.005,show.legend=FALSE) + 
  scale_fill_manual(values = c("darkgreen", "green3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "MSE (\u03b2 and \u03b3)",
       x="MSE",y="# of people")

pcorr <- de2preds %>%
  ggplot(mapping=aes(x=r,fill=condition)) +
  geom_histogram(alpha=0.7,colour="black",binwidth=0.005,show.legend=FALSE) + 
  scale_fill_manual(values = c("darkgreen", "green3")) +
  facet_wrap(~condition,ncol=1) +
  theme_bw() +
  labs(title = "Correlation (\u03b2 and \u03b3)",
       x="r",y="# of people")

p <- grid.arrange(prmse,pcorr,ncol=2)

p

ggsave("figures/exp2_good_beta_gamma_fits_adj.png",plot=p,device="png",
       width=15,height=10, units="cm")

```

# Aggregate fits

We can also look at the parameter values for the aggregate fits. 

```{r aggregatefits_peaked, echo=FALSE, fig.height=3}
dagg <- read.csv(file=here("datafiles/exp2all_good_aggregate_fits_adj.csv")) %>% as_tibble()
dagg_un <- dagg %>% filter(condition=="uniform")
dagg_p <- dagg %>% filter(condition=="peaked")

# prediction assuming uniform prior
x <- c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)
pp <- x^4*(1-x)
py <- pp/sum(pp)

# prediction assuming peaked prior
pry <- c(0,0,0,0,0,0.08,0.08,0.2,0.6,0.04,0)
prpy <- (pry)*x^4*(1-x)
ppy <- prpy/sum(prpy)

# prediction assuming best fits, peaked
beta <- dagg_p$beta[dagg_p$fitted=="two"]
gamma <- dagg_p$gamma[dagg_p$fitted=="two"]
delta <- gamma
prpybest <- (beta*pry+(1-beta)*rep(1/11,11))*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppy,ppyb,pry)

t <- paste0("Pᴇᴀᴋᴇᴅ: \u03b2=",round(beta,digits=2),
  ", \u03b3=",round(gamma,digits=2))

ppeaked_all<- de2peak_lsum %>%
  ggplot(mapping=aes(x=px,y=mean)) +
  #geom_line(data=d,mapping=aes(x=x,y=py),linetype="dotted",
  #          colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppy),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  ylim(0,1) +
  geom_line(colour="darkgreen") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="darkgreen") +
  geom_line(data=d,mapping=aes(x=x,y=pry),
            colour="darkred") + 
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

# prediction assuming best fits, uniform
pry <- rep(1/11,11)
beta <- 1
gamma <- dagg_un$gamma[dagg_un$fitted=="two"]
delta <- gamma
prpybest <- (beta*pry)*
  (x^(gamma*4))*(1-x)^delta
ppyb = prpybest/sum(prpybest)
d <- tibble(x,py,ppyb,pry)

t <- paste0("Uɴɪғᴏʀᴍ: \u03b3=",round(gamma,digits=2))

puniform_all<- de2unif_lsum %>%
  ggplot(mapping=aes(x=ux,y=mean)) +
  geom_line(data=d,mapping=aes(x=x,y=py),linetype="solid",
            colour="darkgray") +
  geom_line(data=d,mapping=aes(x=x,y=ppyb),linetype="dotted",
            colour="black") +
  ylim(0,1) +
  geom_line(colour="green3") + 
  geom_errorbar(mapping = aes(ymin = mean-sderr, ymax = mean+sderr),
                width=0.02,colour="green3") +
  geom_line(data=d,mapping=aes(x=x,y=pry),
            colour="darkred") + 
  theme_bw() +
  labs(title = t,x="Proportion of red",y="Probability")

p <- grid.arrange(ppeaked_all,puniform_all,ncol=2)

ggsave("figures/exp2_good_beta_gamma_aggregate_fits_adj.png",plot=p,device="png",
       width=16,height=8, units="cm")
```
