---
title: "Creation of data files for analysis"
author: "Andrew Perfors"
output: html_document
---

This creates the data files we'll need for subsequent analyses.

```{r setup, include=FALSE}
# We'll begin by loading up the libraries and data we need, as always.
knitr::opts_chunk$set(echo = TRUE)

# loading the libraries
library(tidyverse)
library(here)
library(ggplot2)
library(gridExtra)
library(rminer)

# load the full datasets
de1raw <- read.csv(file=here("Experiment1_Andy.csv")) %>% as_tibble()
# remove people who failed the bot check
bad <- de1raw %>% filter(botCheck==0 | actuallyEstimated==0)
badpeople <- bad$pID
de1 <- de1raw %>% filter(!(pID %in% badpeople))
bad <- de1raw %>% filter(pID %in% badpeople)
de1$pID <- as.factor(de1$pID)

# write the two main datasets
write.csv(bad,"datafiles/exp1_bad_data.csv")
write.csv(de1,"datafiles/exp1_good_data.csv")


# split by condition
de1five <- de1 %>% filter(condition=="five")
de1un <- de1 %>% filter(condition=="unlimited") %>% 
  mutate(selected = seenRed+seenBlue)
de1all <- de1 %>% filter(condition=="all") %>% 
  mutate(selected = seenRed+seenBlue)
write.csv(de1five,"datafiles/exp1_five_data.csv")
write.csv(de1un,"datafiles/exp1_un_data.csv")
write.csv(de1all,"datafiles/exp1_all_data.csv")

# make the priors all nonzero
de1aprior_long <- de1all %>%
  filter(section=="prior") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de1aprior_long$x <- as.numeric(str_sub(de1aprior_long$x,2,10))/100

de1aprior_long_adj <- de1aprior_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de1aprior_adj <- de1aprior_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de1aprior_old <- de1all %>% filter(section=="prior")
de1aprior_old <- de1aprior_old %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de1aprior_new <- merge(de1aprior_old,de1aprior_adj) %>%
  select(pID,condition,section,seenRed,seenBlue,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,time,
         chipsOrder,actuallyEstimated,selected)

de1all_adj <- de1all %>% filter(section!="prior") 
de1all_adj <- rbind(de1all_adj,de1aprior_new)

# make the five all nonzero
de1afive_long <- de1all_adj %>%
  filter(section=="five") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de1afive_long$x <- as.numeric(str_sub(de1afive_long$x,2,10))/100

de1afive_long_adj <- de1afive_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de1afive_adj <- de1afive_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de1afive_old <- de1all_adj %>% filter(section=="five")
de1afive_old <- de1afive_old %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de1afive_new <- merge(de1afive_old,de1afive_adj) %>%
  select(pID,condition,section,seenRed,seenBlue,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,time,
         chipsOrder,actuallyEstimated,selected)

de1all_adj <- de1all_adj %>% filter(section!="five") 
de1all_adj <- rbind(de1all_adj,de1afive_new)

# make the unlimited all nonzero
de1aun_long <- de1all_adj %>%
  filter(section=="unlimited") %>%
  select(pID,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID),names_to="x",values_to="pry")
de1aun_long$x <- as.numeric(str_sub(de1aun_long$x,2,10))/100

de1aun_long_adj <- de1aun_long %>%
  group_by(pID) %>%
  mutate(adjpry = pry+0.01) %>%
  mutate(apry = adjpry/sum(adjpry)) %>%
  ungroup() %>%
  mutate(nx = paste0("e",x*100)) %>%
  select(pID,nx,apry) 

de1aun_adj <- de1aun_long_adj %>%
  pivot_wider(names_from=nx,values_from=apry)

de1aun_old <- de1all_adj %>% filter(section=="unlimited")
de1aun_old <- de1aun_old %>%
  select(-c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100))

de1aun_new <- merge(de1aun_old,de1aun_adj) %>%
  select(pID,condition,section,seenRed,seenBlue,e0,e10,e20,e30,e40,
         e50,e60,e70,e80,e90,e100,age,gender,botCheck,time,
         chipsOrder,actuallyEstimated,selected)

de1all_adj <- de1all_adj %>% filter(section!="unlimited") 
de1all_adj <- rbind(de1all_adj,de1aun_new)

write.csv(de1all_adj,"datafiles/exp1_all_data_adj.csv")

```


## Condition 3 (ALL)

This contains the code to fit individuals in four different ways. 

1. Fit $\beta$, $\gamma$, and $\delta$. Output is in `exp1all_five_allfits.csv`

2. Fit beta and one variable ($\gamma$) which is the same for $\gamma$ and $\delta$, i.e., it enforces them to be the same. Output is in `exp1all_five_twofits.csv`

3. Fit only $\beta$, and force $\gamma=\delta=1$. The point of this is to see if the fits we get on $\beta$ which imply they are ignoring the prior are an artefact of also fitting $\delta$ and $\gamma$. Output is in `exp1all_five_betafits.csv`

4. Fit only $\gamma$, and assume that $\beta=1$. The point of this is the opposite of #3. Output is in `exp1all_five_gammafits_adj.csv`

```{r fitthingsfive}
# uncomment this to make it do it on the adjusted dataset
de1all <- de1all_adj

de1all_long <- de1all %>% 
  select(-c(condition,age,gender,botCheck,time,chipsOrder,
            actuallyEstimated,selected)) %>%
  pivot_longer(cols=c(e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100),
               names_to="x",values_to="y")
de1all_long$x <- as.numeric(str_sub(de1all_long$x,2,10))/100

# the function that fits beta, gamma, and delta
frfiveall <- function(ps,d) {
  dfive <- d %>% filter(section=="five")
  dprior <- d %>% filter(section=="prior")
   beta <- ps[1]
   gamma <- ps[2]
   delta <- ps[3]
   x <- dfive$x
   y <- dfive$y
   pry <- dprior$y
   y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(delta*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits beta and gamma/delta as one
frfivetwo <- function(ps,d) {
  dfive <- d %>% filter(section=="five")
  dprior <- d %>% filter(section=="prior")
   beta <- ps[1]
   gamma <- ps[2]
   x <- dfive$x
   y <- dfive$y
   pry <- dprior$y
      y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only beta
frfivebeta <- function(ps,d) {
  dfive <- d %>% filter(section=="five")
  dprior <- d %>% filter(section=="prior")
  gamma <- 1
   beta <- ps[1]
   x <- dfive$x
   y <- dfive$y
   pry <- dprior$y
    y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only gamma
frfivegamma <- function(ps,d) {
  dfive <- d %>% filter(section=="five")
  dprior <- d %>% filter(section=="prior")
   gamma <- ps[1]
   x <- dfive$x
   y <- dfive$y
   pry <- dprior$y
      y <- y/sum(y)
   pry <- pry/sum(pry)
   likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
   prior <- pry
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# fitting delta, gamma, and beta
ddfiveall <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1,1),frfiveall,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001,0.0000001),
                          upper=c(0.9999999,50,50))))

de1all_fiveall <- de1all %>% filter(section=="five")
de1all_fiveall$beta <- NA
de1all_fiveall$gamma <- NA
de1all_fiveall$delta <- NA
de1all_fiveall$value <- NA

for (i in 1:nrow(de1all_fiveall)) {
  pid <- ddfiveall$pID[i]
  de1all_fiveall$beta[de1all_fiveall$pID==pid] <-
    ddfiveall$fit[[i]]$par[1]
  de1all_fiveall$gamma[de1all_fiveall$pID==pid] <-
    ddfiveall$fit[[i]]$par[2]
  de1all_fiveall$delta[de1all_fiveall$pID==pid] <-
    ddfiveall$fit[[i]]$par[3]
  de1all_fiveall$value[de1all_fiveall$pID==pid] <-
    ddfiveall$fit[[i]]$value[1]
}

write.csv(de1all_fiveall,"datafiles/exp1all_five_allfits_adj.csv")

# fitting delta/gamma, and beta
ddfivetwo <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),frfivetwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

de1all_fivetwo <- de1all %>% filter(section=="five")
de1all_fivetwo$beta <- NA
de1all_fivetwo$gamma <- NA
de1all_fivetwo$value <- NA

for (i in 1:nrow(de1all_fivetwo)) {
  pid <- ddfivetwo$pID[i]
  de1all_fivetwo$beta[de1all_fivetwo$pID==pid] <-
    ddfivetwo$fit[[i]]$par[1]
  de1all_fivetwo$gamma[de1all_fivetwo$pID==pid] <-
    ddfivetwo$fit[[i]]$par[2]
  de1all_fivetwo$value[de1all_fivetwo$pID==pid] <-
    ddfivetwo$fit[[i]]$value[1]
}

write.csv(de1all_fivetwo,"datafiles/exp1all_five_twofits_adj.csv")

# fitting only beta
ddfivebeta <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5),frfivebeta,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(0.9999999))))

de1all_fivebeta <- de1all %>% filter(section=="five")
de1all_fivebeta$beta <- NA
de1all_fivebeta$value <- NA

for (i in 1:nrow(de1all_fivebeta)) {
    pid <- ddfivebeta$pID[i]
  de1all_fivebeta$beta[de1all_fivebeta$pID==pid] <-
    ddfivebeta$fit[[i]]$par[1]
  de1all_fivebeta$value[de1all_fivebeta$pID==pid] <-
    ddfivebeta$fit[[i]]$value[1]
}

write.csv(de1all_fivebeta,"datafiles/exp1all_five_betafits_adj.csv")

# fitting only gamma
ddfivegamma <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1),frfivegamma,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(50))))

de1all_fivegamma <- de1all %>% filter(section=="five")
de1all_fivegamma$gamma <- NA
de1all_fivegamma$value <- NA

for (i in 1:nrow(de1all_fivegamma)) {
    pid <- ddfivegamma$pID[i]
  de1all_fivegamma$gamma[de1all_fivegamma$pID==pid] <-
    ddfivegamma$fit[[i]]$par[1]
  de1all_fivegamma$value[de1all_fivegamma$pID==pid] <-
    ddfivegamma$fit[[i]]$value[1]
}

write.csv(de1all_fivegamma,"datafiles/exp1all_five_gammafits_adj.csv")

```

Now we're going to do the same thing with the unlimited data points.

1. Fit $\beta$, $\gamma$, and $\delta$. Output is in `exp1all_un_allfits.csv`

2. Fit beta and one variable ($\gamma$) which is the same for $\gamma$ and $\delta$, i.e., it enforces them to be the same. Output is in `exp1all_un_twofits.csv`

3. Fit only $\beta$, and force $\gamma=\delta=1$. The point of this is to see if the fits we get on $\beta$ which imply they are ignoring the prior are an artefact of also fitting $\delta$ and $\gamma$. Output is in `exp1all_un_betafits.csv`

4. Fit only $\gamma$, and assume that $\beta=1$. The point of this is the opposite of #3. Output is in `exp1all_un_gammafits_adj.csv`


```{r fitthingsun}

# the function that fits beta, gamma, and delta
frunall <- function(ps,d) {
  dun <- d %>% filter(section=="unlimited")
  dprior <- d %>% filter(section=="prior")
   beta <- ps[1]
   gamma <- ps[2]
   delta <- ps[3]
   x <- dun$x
   y <- dun$y
   pry <- dprior$y
   y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   nr <- dun$seenRed[1]
   nb <- dun$seenBlue[1]
   likelihood <- x^(gamma*nr)*(1-x)^(delta*nb)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits beta and gamma/delta as one
fruntwo <- function(ps,d) {
  dun <- d %>% filter(section=="unlimited")
  dprior <- d %>% filter(section=="prior")
   beta <- ps[1]
   gamma <- ps[2]
   x <- dun$x
   y <- dun$y
   pry <- dprior$y
   y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   nr <- dun$seenRed[1]
   nb <- dun$seenBlue[1]
   likelihood <- x^(gamma*nr)*(1-x)^(gamma*nb)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits only beta
frunbeta <- function(ps,d) {
  dun <- d %>% filter(section=="unlimited")
  dprior <- d %>% filter(section=="prior")
   beta <- ps[1]
   gamma <- 1
   x <- dun$x
   y <- dun$y
   pry <- dprior$y
   y <- y/sum(y)
   pry <- pry/sum(pry)
   uny <- rep(1/11,11)
   nr <- dun$seenRed[1]
   nb <- dun$seenBlue[1]
   likelihood <- x^(gamma*nr)*(1-x)^(gamma*nb)
   prior <- (beta*pry+(1-beta)*uny)
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# the function that fits onlygamma
frungamma <- function(ps,d) {
  dun <- d %>% filter(section=="unlimited")
  dprior <- d %>% filter(section=="prior")
   gamma <- ps[1]
   x <- dun$x
   y <- dun$y
   pry <- dprior$y
   y <- y/sum(y)
   pry <- pry/sum(pry)
   nr <- dun$seenRed[1]
   nb <- dun$seenBlue[1]
   likelihood <- x^(gamma*nr)*(1-x)^(gamma*nb)
   prior <- pry
   result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
   return(result)
}

# fitting delta, gamma, and beta
ddunall <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1,1),frunall,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001,0.0000001),
                          upper=c(0.9999999,50,50))))

de1all_unall <- de1all %>% filter(section=="unlimited")
de1all_unall$beta <- NA
de1all_unall$gamma <- NA
de1all_unall$delta <- NA
de1all_unall$value <- NA

for (i in 1:nrow(de1all_unall)) {
  pid <- ddunall$pID[i]
  de1all_unall$beta[de1all_unall$pID==pid] <-
    ddunall$fit[[i]]$par[1]
  de1all_unall$gamma[de1all_unall$pID==pid] <-
    ddunall$fit[[i]]$par[2]
  de1all_unall$delta[de1all_unall$pID==pid] <-
    ddunall$fit[[i]]$par[3]
  de1all_unall$value[de1all_unall$pID==pid] <-
    ddunall$fit[[i]]$value[1]
}

write.csv(de1all_unall,"datafiles/exp1all_un_allfits_adj.csv")

# fitting delta/gamma, and beta
dduntwo <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1,1),fruntwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

de1all_untwo <- de1all %>% filter(section=="unlimited")
de1all_untwo$beta <- NA
de1all_untwo$gamma <- NA
de1all_untwo$value <- NA

for (i in 1:nrow(de1all_untwo)) {
  pid <- dduntwo$pID[i]
  de1all_untwo$beta[de1all_untwo$pID==pid] <-
    dduntwo$fit[[i]]$par[1]
  de1all_untwo$gamma[de1all_untwo$pID==pid] <-
    dduntwo$fit[[i]]$par[2]
  de1all_untwo$value[de1all_untwo$pID==pid] <-
    dduntwo$fit[[i]]$value[1]
}

write.csv(de1all_untwo,"datafiles/exp1all_un_twofits_adj.csv")

# fitting only beta
ddunbeta <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5),frunbeta,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(0.9999999))))

de1all_unbeta <- de1all %>% filter(section=="unlimited")
de1all_unbeta$beta <- NA
de1all_unbeta$value <- NA

for (i in 1:nrow(de1all_unbeta)) {
  pid <- ddunbeta$pID[i]
  de1all_unbeta$beta[de1all_unbeta$pID==pid] <-
    ddunbeta$fit[[i]]$par[1]
  de1all_unbeta$value[de1all_unbeta$pID==pid] <-
    ddunbeta$fit[[i]]$value[1]
}

write.csv(de1all_unbeta,"datafiles/exp1all_un_betafits_adj.csv")

# fitting only gamma
ddungamma <- de1all_long %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1),frungamma,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(50))))

de1all_ungamma <- de1all %>% filter(section=="unlimited")
de1all_ungamma$gamma <- NA
de1all_ungamma$value <- NA

for (i in 1:nrow(de1all_ungamma)) {
  pid <- ddungamma$pID[i]
  de1all_ungamma$gamma[de1all_ungamma$pID==pid] <-
    ddungamma$fit[[i]]$par[1]
  de1all_ungamma$value[de1all_ungamma$pID==pid] <-
    ddungamma$fit[[i]]$value[1]
}

write.csv(de1all_ungamma,"datafiles/exp1all_un_gammafits_adj.csv")

```


## Calculate aggregate best-fit parameters

This contains the code for the aggregate best fits in different ways. First we'll do it just for the section with five data points (4 red and 1 blue). It does it for all of the four possibilities above. 

```{r fitthingsaggregate}
# make dataset with aggregate results
de1a_long <- de1all %>%
  select(pID,section,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID,section),names_to="x",values_to="pry")
de1a_long$x <- as.numeric(str_sub(de1a_long$x,2,10))/100

de1_lsum <- de1a_long %>%
  group_by(section,x) %>%
  summarise(y=mean(pry)) %>%
  ungroup()

nr <- mean(de1all$seenRed[de1all$section=="unlimited"])
nb <- mean(de1all$seenBlue[de1all$section=="unlimited"])

section <- c("prior","five","unlimited")
seenRed <- c(0,4,nr)
seenBlue <- c(0,1,nb)
nd <- tibble(section,seenRed,seenBlue)

de1_lsum <- merge(de1_lsum,nd)
write.csv(de1_lsum,"datafiles/exp1all_aggregate_curves_adj.csv")

# fitting delta, gamma, and beta on unlimited
ddaggall_un <- optim(c(0.5,1,1),frunall,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001,0.0000001),
                  upper=c(0.9999999,50,50))

# fitting gamma and beta on unlimited
ddaggtwo_un <- optim(c(0.5,1),fruntwo,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001),
                  upper=c(0.9999999,50))

# fitting beta on unlimited
ddaggbeta_un <- optim(c(0.5),frunbeta,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(0.9999999))

# fitting gamma on unlimited
ddagggamma_un <- optim(c(1),frungamma,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(50))

# fitting delta, gamma, and beta on five
ddaggall_five <- optim(c(0.5,1,1),frfiveall,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001,0.0000001),
                  upper=c(0.9999999,50,50))

# fitting gamma and beta on five
ddaggtwo_five <- optim(c(0.5,1),frfivetwo,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001,0.0000001),
                  upper=c(0.9999999,50))

# fitting beta on five
ddaggbeta_five <- optim(c(0.5),frfivebeta,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(0.9999999))

# fitting gamma on five
ddagggamma_five <- optim(c(1),frfivegamma,d=de1_lsum,method="L-BFGS-B",
                  lower=c(0.0000001),upper=c(50))


section <- c(rep("unlimited",4),rep("five",4))
fitted <- c("all","two","beta","gamma","all","two","beta","gamma")
beta <- c(ddaggall_un$par[1],ddaggtwo_un$par[1],ddaggbeta_un$par[1],NA,
          ddaggall_five$par[1],ddaggtwo_five$par[1],ddaggbeta_five$par[1],NA)
gamma <- c(ddaggall_un$par[2],ddaggtwo_un$par[2],NA,ddagggamma_un$par[1],
          ddaggall_five$par[2],ddaggtwo_five$par[2],NA,ddagggamma_five$par[1])
delta <- c(ddaggall_un$par[3],NA,NA,NA,ddaggall_five$par[3],NA,NA,NA)
value <- c(ddaggall_un$value,ddaggtwo_un$value,ddaggbeta_un$value,
           ddagggamma_un$value,ddaggall_five$value,ddaggtwo_five$value,
           ddaggbeta_five$value,ddagggamma_five$value)
dagg <- tibble(section,fitted,beta,gamma,delta,value)
write.csv(dagg,"datafiles/exp1all_aggregate_fits_adj.csv")
```