---
title: "Plausibility"
author: "Andrew Perfors"
output: html_document
---

The goal of this is to determine whether our approach is plausible. What we do is for each experiment, take the inferred parameters ($\beta$ and $\gamma$) and priors for each person, and use those to generate posteriors. Then give the model the priors and generated posteriors and see if the parameters it identifies are the same as the ones used to generate the posteriors.

```{r setup, include=FALSE}
# We'll begin by loading up the libraries and data we need, as always.
knitr::opts_chunk$set(echo = TRUE)

# loading the libraries
library(tidyverse)
library(here)
library(ggplot2)
library(gridExtra)
library(rminer)
```

## Experiment 1

The first step is to generate new posteriors for each person given the $\beta$ and $\gamma$ parameters we inferred. We consider the two ones in the Mᴀɪɴ experiment, with either Five or Unlimited chips.

```{r expt1posteriors, echo=FALSE}
d1f <- read.csv(file=here("datafiles/exp1all_five_twofits_adj.csv")) %>% as_tibble()
d1u <- read.csv(file=here("datafiles/exp1all_un_twofits_adj.csv")) %>% as_tibble()

d1f_long <- d1f %>%
  select(pID,beta,gamma,value,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID,beta,gamma,value),names_to="x",values_to="prior")
d1f_long$x <- as.numeric(str_sub(d1f_long$x,2,10))/100

d1u_long <- d1u %>%
  select(pID,beta,gamma,value,seenRed,seenBlue,
         e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID,beta,gamma,value,seenRed,seenBlue),
               names_to="x",values_to="prior")
d1u_long$x <- as.numeric(str_sub(d1u_long$x,2,10))/100

d1f_post <- d1f_long %>%
  group_by(pID) %>%
  mutate(pst = (beta*prior+(1-beta)*rep(1/11,11))*
           (x^(gamma*4)*(1-x)^gamma)) %>%
  mutate(genpost = pst/sum(pst)) %>%
  ungroup()
d1f_post$pst <- NULL

d1u_post <- d1u_long %>%
  group_by(pID) %>%
  mutate(pst = (beta*prior+(1-beta)*rep(1/11,11))*
           (x^(gamma*seenRed)*(1-x)^(gamma*seenBlue))) %>%
  mutate(genpost = pst/sum(pst)) %>%
  ungroup()
d1u_post$pst <- NULL
```

Then, for person we want to now infer $\beta$ and $\gamma$ based on their prior and generated posterior.

```{r exp1inferparams, echo=FALSE}
# the function that fits beta and gamma/delta as one for FIVE condition
frfivetwo <- function(ps,d) {
  beta <- ps[1]
  gamma <- ps[2]
  x <- d$x
  y <- d$genpost
  pry <- d$prior
  y <- y/sum(y)
  pry <- pry/sum(pry)
  uny <- rep(1/11,11)
  likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
  prior <- (beta*pry+(1-beta)*uny)
  result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
  return(result)
}

# the function that fits beta and gamma/delta as one for UNLIMITED condition
fruntwo <- function(ps,d) {
  beta <- ps[1]
  gamma <- ps[2]
  x <- d$x
  y <- d$genpost
  pry <- d$prior
  y <- y/sum(y)
  pry <- pry/sum(pry)
  uny <- rep(1/11,11)
  nr <- d$seenRed[1]
  nb <- d$seenBlue[1]
  likelihood <- x^(gamma*nr)*(1-x)^(gamma*nb)
  prior <- (beta*pry+(1-beta)*uny)
  result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
  return(result)
}

# fitting delta/gamma, and beta for FIVE condition
d1f_fit <- d1f_post %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),frfivetwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

d1f_post$infbeta <- NA
d1f_post$infgamma <- NA
d1f_post$infvalue <- NA

for (i in 1:nrow(d1f_fit)) {
  nid <- d1f_fit$pID[i]
  d1f_post$infbeta[d1f_post$pID==nid] <-d1f_fit$fit[[i]]$par[1]
  d1f_post$infgamma[d1f_post$pID==nid] <-d1f_fit$fit[[i]]$par[2]
  d1f_post$infvalue[d1f_post$pID==nid] <-d1f_fit$fit[[i]]$value[1]
}

# fitting delta/gamma, and beta for UNLIMITED condition
d1u_fit <- d1u_post %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),fruntwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

d1u_post$infbeta <- NA
d1u_post$infgamma <- NA
d1u_post$infvalue <- NA

for (i in 1:nrow(d1u_fit)) {
  nid <- d1u_fit$pID[i]
  d1u_post$infbeta[d1u_post$pID==nid] <- d1u_fit$fit[[i]]$par[1]
  d1u_post$infgamma[d1u_post$pID==nid] <-d1u_fit$fit[[i]]$par[2]
  d1u_post$infvalue[d1u_post$pID==nid] <-d1u_fit$fit[[i]]$value[1]
}

write.csv(d1f_post,"datafiles/exp1_all_five_plausibility.csv")
write.csv(d1u_post,"datafiles/exp1_all_un_plausibility.csv")
```

Now we want to see the accuracy of these things.

```{r exp1accuracy, echo=FALSE}
d1f_post <- d1f_post %>%
  mutate(berror = abs(beta-infbeta)) %>%
  mutate(gerror = abs(gamma-infgamma))

d1u_post <- d1u_post %>%
  mutate(berror = abs(beta-infbeta)) %>%
  mutate(gerror = abs(gamma-infgamma))

# create short datasets
d1f_short <- d1f_post %>%
  filter(x==0.0) %>%
  select(-c(x,prior,genpost))

d1u_short <- d1u_post %>%
  filter(x==0.0) %>%
  select(-c(x,prior,genpost))

d1f_b <- d1f_short %>%
  ggplot(mapping=aes(x=beta,y=infbeta)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.01,size=2) +
  theme_bw() +
  labs(title = "Exp 1, Five chips: \u03b2 accuracy",
       x="Beta",y="Inferred beta")

d1f_g <- d1f_short %>%
  ggplot(mapping=aes(x=gamma,y=infgamma)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.5,size=2) +
  theme_bw() +
  labs(title = "Exp 1, Five chips: \u03b3 accuracy",
       x="Gamma",y="Inferred gamma")

d1u_b <- d1u_short %>%
  ggplot(mapping=aes(x=beta,y=infbeta)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.01,size=2) +
  theme_bw() +
  labs(title = "Exp 1, Unlimited: \u03b2 accuracy",
       x="Beta",y="Inferred beta")

d1u_g <- d1u_short %>%
  ggplot(mapping=aes(x=gamma,y=infgamma)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.5,size=2) +
  theme_bw() +
  labs(title = "Exp 1, Unlimited: \u03b3 accuracy",
       x="Gamma",y="Inferred gamma")

p <- grid.arrange(d1f_b,d1f_g,ncol=2)
ggsave("figures/exp1_plausibility_five.png",plot=p,device="png",
       width=16,height=6, units="cm")

p <- grid.arrange(d1u_b,d1u_g,ncol=2)
ggsave("figures/exp1_plausibility_un.png",plot=p,device="png",
       width=16,height=6, units="cm")

# calculating correlations
d1f_bcor <- cor.test(d1f_short$beta,d1f_short$infbeta)
d1f_gcor <- cor.test(d1f_short$gamma,d1f_short$infgamma)
d1u_bcor <- cor.test(d1u_short$beta,d1u_short$infbeta)
d1u_gcor <- cor.test(d1u_short$gamma,d1u_short$infgamma)
```

For Five chips, `r round(100*sum(d1f_short$berror<0.1)/nrow(d1f_short),1)`% of the inferred beta were less than 0.1 off the original $\beta$ (participant ids were `r d1f_short$pID[d1f_short$berror>=0.1]`). The correlation of $\beta$ to inferred $\beta$ was r=`r round(d1f_bcor$estimate[[1]],5)`, p=`r round(d1f_bcor$p.value[1],3)`.

Also, `r round(100*sum(d1f_short$gerror<0.1)/nrow(d1f_short),1)`% of the inferred $\gamma$ were less than 0.1 off (participant ids were `r d1f_short$pID[d1f_short$gerror>=0.1]`). The correlation of $\gamma$ to inferred $\gamma$ was r=`r round(d1f_gcor$estimate[[1]],5)`, p=`r round(d1f_gcor$p.value[1],3)`.

For Unlimited chips, `r round(100*sum(d1u_short$berror<0.1)/nrow(d1u_short),1)`% of the inferred beta were less than 0.1 off the original $\beta$ (participant ids were `r d1u_short$pID[d1u_short$berror>=0.1]`). The correlation of $\beta$ to inferred $\beta$ was r=`r round(d1u_bcor$estimate[[1]],5)`, p=`r round(d1u_bcor$p.value[1],3)`.

Also, `r round(100*sum(d1u_short$gerror<0.1)/nrow(d1u_short),1)`% of the inferred $\gamma$ were less than 0.1 off (participant ids were `r d1u_short$pID[d1u_short$gerror>=0.1]`). The correlation of $\gamma$ to inferred $\gamma$ was r=`r round(d1u_gcor$estimate[[1]],5)`, p=`r round(d1u_gcor$p.value[1],3)`.


## Experiment 2

The first step is to generate new posteriors for each person given the $\beta$ and $\gamma$ parameters we inferred. There were two conditions, Pᴇᴀᴋᴇᴅ and Uɴɪғᴏʀᴍ

```{r expt2posteriors, echo=FALSE}
d2p <- read.csv(file=here("datafiles/exp2_peaked_twofits_adj.csv")) %>% as_tibble()
d2u <- read.csv(file=here("datafiles/exp2_uniform_twofits_adj.csv")) %>%
  as_tibble()

d2p_long <- d2p %>%
  select(pID,beta,gamma,value,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID,beta,gamma,value),names_to="x",values_to="prior")
d2p_long$x <- as.numeric(str_sub(d2p_long$x,2,10))/100

d2u_long <- d2u %>%
  select(pID,gamma,value,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID,gamma,value),
               names_to="x",values_to="prior")
d2u_long$x <- as.numeric(str_sub(d2u_long$x,2,10))/100

d2p_post <- d2p_long %>%
  group_by(pID) %>%
  mutate(pst = (beta*prior+(1-beta)*rep(1/11,11))*
           (x^(gamma*4)*(1-x)^gamma)) %>%
  mutate(genpost = pst/sum(pst)) %>%
  ungroup()
d2p_post$pst <- NULL

d2u_post <- d2u_long %>%
  group_by(pID) %>%
  mutate(pst = (rep(1/11,11))*
           (x^(gamma*4)*(1-x)^(gamma*1))) %>%
  mutate(genpost = pst/sum(pst)) %>%
  ungroup()
d2u_post$pst <- NULL
```

Then, for each person we want to now infer $\beta$ and $\gamma$ based on their prior and generated posterior. (For the Uniform condition we only infer $\gamma$).

```{r exp2inferparams, echo=FALSE}
# the function that fits gamma for the uniform condition
frgammaonly <- function(ps,d) {
  gamma <- ps[1]
  x <- d$x
  y <- d$genpost
  pry <- d$prior
  y <- y/sum(y)
  pry <- pry/sum(pry)
  likelihood <- x^(gamma*4)*(1-x)^(gamma*1)
  prior <- rep(1/11,11)
  result <- sum((y - (likelihood*prior)/sum(likelihood*prior))^2)
  return(result)
}


# fitting delta/gamma, and beta for PEAKED condition
d2p_fit <- d2p_post %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),frfivetwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

d2p_post$infbeta <- NA
d2p_post$infgamma <- NA
d2p_post$infvalue <- NA

for (i in 1:nrow(d2p_fit)) {
  nid <- d2p_fit$pID[i]
  d2p_post$infbeta[d2p_post$pID==nid] <-d2p_fit$fit[[i]]$par[1]
  d2p_post$infgamma[d2p_post$pID==nid] <-d2p_fit$fit[[i]]$par[2]
  d2p_post$infvalue[d2p_post$pID==nid] <-d2p_fit$fit[[i]]$value[1]
}

# fitting gamma for UNIFORM condition
d2u_fit <- d2u_post %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(1),frgammaonly,d=data,method="L-BFGS-B",
                          lower=c(0.0000001),
                          upper=c(50))))

d2u_post$infgamma <- NA
d2u_post$infvalue <- NA

for (i in 1:nrow(d2u_fit)) {
  nid <- d2u_fit$pID[i]
  d2u_post$infgamma[d2u_post$pID==nid] <-d2u_fit$fit[[i]]$par[1]
  d2u_post$infvalue[d2u_post$pID==nid] <-d2u_fit$fit[[i]]$value[1]
}

write.csv(d2p_post,"datafiles/exp2_peaked_plausibility.csv")
write.csv(d2u_post,"datafiles/exp2_uniform_plausibility.csv")
```

Now we want to see the accuracy of these things.

```{r exp2accuracy, echo=FALSE}
d2p_post <- d2p_post %>%
  mutate(berror = abs(beta-infbeta)) %>%
  mutate(gerror = abs(gamma-infgamma))

d2u_post <- d2u_post %>%
  mutate(gerror = abs(gamma-infgamma))

# create short datasets
d2p_short <- d2p_post %>%
  filter(x==0.0) %>%
  select(-c(x,prior,genpost))

d2u_short <- d2u_post %>%
  filter(x==0.0) %>%
  select(-c(x,prior,genpost))

d2p_b <- d2p_short %>%
  ggplot(mapping=aes(x=beta,y=infbeta)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.01,size=2) +
  theme_bw() +
  labs(title = "Exp 2, Pᴇᴀᴋᴇᴅ: \u03b2 accuracy",
       x="Beta",y="Inferred beta")

d2p_g <- d2p_short %>%
  ggplot(mapping=aes(x=gamma,y=infgamma)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.5,size=2) +
  theme_bw() +
  labs(title = "Exp 2, Pᴇᴀᴋᴇᴅ: \u03b3 accuracy",
       x="Gamma",y="Inferred gamma")

d2u_g <- d2u_short %>%
  ggplot(mapping=aes(x=gamma,y=infgamma)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.5,size=2) +
  theme_bw() +
  labs(title = "Exp 2, Uɴɪғᴏʀᴍ: \u03b3 accuracy",
       x="Gamma",y="Inferred gamma")

p <- grid.arrange(d2p_b,d2p_g,ncol=2)
ggsave("figures/exp2_plausibility_peaked.png",plot=p,device="png",
       width=16,height=6, units="cm")

p <- grid.arrange(d2u_g,ncol=1)
ggsave("figures/exp2_plausibility_uniform.png",plot=p,device="png",
       width=8,height=6, units="cm")

# calculating correlations
d2p_bcor <- cor.test(d2p_short$beta,d2p_short$infbeta)
d2p_gcor <- cor.test(d2p_short$gamma,d2p_short$infgamma)
d2u_gcor <- cor.test(d2u_short$gamma,d2u_short$infgamma)
```


For Pᴇᴀᴋᴇᴅ, `r round(100*sum(d2p_short$berror<0.1)/nrow(d2p_short),1)`% of the inferred beta were less than 0.1 off the original $\beta$ (participant ids were `r d2p_short$pID[d2p_short$berror>=0.1]`). The correlation of $\beta$ to inferred $\beta$ was r=`r round(d2p_bcor$estimate[[1]],5)`, p=`r round(d2p_bcor$p.value[1],3)`.

Also, `r round(100*sum(d2p_short$gerror<0.1)/nrow(d2p_short),1)`% of the inferred $\gamma$ were less than 0.1 off (participant ids were `r d2p_short$pID[d2p_short$gerror>=0.1]`). The correlation of $\gamma$ to inferred $\gamma$ was r=`r round(d2p_gcor$estimate[[1]],5)`, p=`r round(d2p_gcor$p.value[1],3)`.

For Uɴɪғᴏʀᴍ, `r round(100*sum(d2u_short$gerror<0.1)/nrow(d2u_short),1)`% of the inferred gamma were less than 0.1 off the original gamma (participant ids were `r d2u_short$pID[d2u_short$gerror>=0.1]`). The correlation of $\gamma$ to inferred $\gamma$ was r=`r round(d2u_gcor$estimate[[1]],5)`, p=`r round(d2u_gcor$p.value[1],3)`.

## Experiment 3

The first step is to generate new posteriors for each person given the $\beta$ and $\gamma$ parameters we inferred. There were two conditions, Esᴛɪᴍᴀᴛᴇᴅ and Gɪᴠᴇɴ

```{r expt3posteriors, echo=FALSE}
d3e <- read.csv(file=here("datafiles/exp3est_twofits_adj.csv")) %>% as_tibble()
d3g <- read.csv(file=here("datafiles/exp3given_twofits_adj.csv")) %>% as_tibble()

d3e_long <- d3e %>%
  select(pID,beta,gamma,value,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID,beta,gamma,value),names_to="x",values_to="prior")
d3e_long$x <- as.numeric(str_sub(d3e_long$x,2,10))/100

d3g_long <- d3g %>%
  select(pID,beta,gamma,value,e0,e10,e20,e30,e40,e50,e60,e70,e80,e90,e100) %>%
  pivot_longer(cols=-c(pID,beta,gamma,value),
               names_to="x",values_to="prior")
d3g_long$x <- as.numeric(str_sub(d3g_long$x,2,10))/100

d3e_post <- d3e_long %>%
  group_by(pID) %>%
  mutate(pst = (beta*prior+(1-beta)*rep(1/11,11))*
           (x^(gamma*4)*(1-x)^gamma)) %>%
  mutate(genpost = pst/sum(pst)) %>%
  ungroup()
d3e_post$pst <- NULL

d3g_post <- d3g_long %>%
  group_by(pID) %>%
  mutate(pst = (beta*prior+(1-beta)*rep(1/11,11))*
           (x^(gamma*4)*(1-x)^gamma)) %>%
  mutate(genpost = pst/sum(pst)) %>%
  ungroup()
d3g_post$pst <- NULL
```

Then, for each person we want to now infer $\beta$ and $\gamma$ based on their prior and generated posterior. 

```{r exp3inferparams, echo=FALSE}

# fitting delta/gamma, and beta for ESTIMATED condition
d3e_fit <- d3e_post %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),frfivetwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

d3e_post$infbeta <- NA
d3e_post$infgamma <- NA
d3e_post$infvalue <- NA

for (i in 1:nrow(d3e_fit)) {
  nid <- d3e_fit$pID[i]
  d3e_post$infbeta[d3e_post$pID==nid] <-d3e_fit$fit[[i]]$par[1]
  d3e_post$infgamma[d3e_post$pID==nid] <-d3e_fit$fit[[i]]$par[2]
  d3e_post$infvalue[d3e_post$pID==nid] <-d3e_fit$fit[[i]]$value[1]
}

# fitting delta/gamma, and beta for GIVEN condition
d3g_fit <- d3g_post %>% 
  nest_by(pID) %>% 
  mutate(fit = list(optim(c(0.5,1),frfivetwo,d=data,method="L-BFGS-B",
                          lower=c(0.0000001,0.0000001),
                          upper=c(0.9999999,50))))

d3g_post$infbeta <- NA
d3g_post$infgamma <- NA
d3g_post$infvalue <- NA

for (i in 1:nrow(d3g_fit)) {
  nid <- d3g_fit$pID[i]
  d3g_post$infbeta[d3g_post$pID==nid] <-d3g_fit$fit[[i]]$par[1]
  d3g_post$infgamma[d3g_post$pID==nid] <-d3g_fit$fit[[i]]$par[2]
  d3g_post$infvalue[d3g_post$pID==nid] <-d3g_fit$fit[[i]]$value[1]
}

write.csv(d3e_post,"datafiles/exp3_estimated_plausibility.csv")
write.csv(d3g_post,"datafiles/exp3_given_plausibility.csv")
```

Now we want to see the accuracy of these things.

```{r exp3accuracy, echo=FALSE}
d3e_post <- d3e_post %>%
  mutate(berror = abs(beta-infbeta)) %>%
  mutate(gerror = abs(gamma-infgamma))

d3g_post <- d3g_post %>%
  mutate(berror = abs(beta-infbeta)) %>%
  mutate(gerror = abs(gamma-infgamma))

# create short datasets
d3e_short <- d3e_post %>%
  filter(x==0.0) %>%
  select(-c(x,prior,genpost))

d3g_short <- d3g_post %>%
  filter(x==0.0) %>%
  select(-c(x,prior,genpost))

d3e_b <- d3e_short %>%
  ggplot(mapping=aes(x=beta,y=infbeta)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.01,size=2) +
  theme_bw() +
  labs(title = "Exp 3, Esᴛɪᴍᴀᴛᴇᴅ: \u03b2 accuracy",
       x="Beta",y="Inferred beta")

d3e_g <- d3e_short %>%
  ggplot(mapping=aes(x=gamma,y=infgamma)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.5,size=2) +
  theme_bw() +
  labs(title = "Exp 3, Esᴛɪᴍᴀᴛᴇᴅ: \u03b3 accuracy",
       x="Gamma",y="Inferred gamma")

d3g_b <- d3g_short %>%
  ggplot(mapping=aes(x=beta,y=infbeta)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.01,size=2) +
  theme_bw() +
  labs(title = "Exp 3, Gɪᴠᴇɴ: \u03b2 accuracy",
       x="Beta",y="Inferred beta")

d3g_g <- d3g_short %>%
  ggplot(mapping=aes(x=gamma,y=infgamma)) +
  geom_jitter(alpha=0.5,colour="blue",width=0.5,size=2) +
  theme_bw() +
  labs(title = "Exp 3, Gɪᴠᴇɴ: \u03b3 accuracy",
       x="Gamma",y="Inferred gamma")

p <- grid.arrange(d3e_b,d3e_g,ncol=2)
ggsave("figures/exp3_plausibility_estimated.png",plot=p,device="png",
       width=16,height=6, units="cm")

p <- grid.arrange(d3g_b,d3g_g,ncol=2)
ggsave("figures/exp3_plausibility_given.png",plot=p,device="png",
       width=16,height=6, units="cm")

# calculating correlations
d3e_bcor <- cor.test(d3e_short$beta,d3e_short$infbeta)
d3e_gcor <- cor.test(d3e_short$gamma,d3e_short$infgamma)
d3g_bcor <- cor.test(d3g_short$beta,d3g_short$infbeta)
d3g_gcor <- cor.test(d3g_short$gamma,d3g_short$infgamma)
```

For Esᴛɪᴍᴀᴛᴇᴅ, `r round(100*sum(d3e_short$berror<0.1)/nrow(d3e_short),1)`% of the inferred beta were less than 0.1 off the original $\beta$ (participant ids were `r d3e_short$pID[d3e_short$berror>=0.1]`). The correlation of $\beta$ to inferred $\beta$ was r=`r round(d3e_bcor$estimate[[1]],5)`, p=`r round(d3e_bcor$p.value[1],3)`.

Also, `r round(100*sum(d3e_short$gerror<0.1)/nrow(d3e_short),1)`% of the inferred $\gamma$ were less than 0.1 off (participant ids were `r d3e_short$pID[d3e_short$gerror>=0.1]`). The correlation of $\gamma$ to inferred $\gamma$ was r=`r round(d3e_gcor$estimate[[1]],5)`, p=`r round(d3e_gcor$p.value[1],3)`.

For Gɪᴠᴇɴ, `r round(100*sum(d3g_short$berror<0.1)/nrow(d3g_short),1)`% of the inferred beta were less than 0.1 off the original $\beta$ (participant ids were `r d3g_short$pID[d3g_short$berror>=0.1]`). The correlation of $\beta$ to inferred $\beta$ was r=`r round(d3g_bcor$estimate[[1]],5)`, p=`r round(d3g_bcor$p.value[1],3)`.

Also, `r round(100*sum(d3g_short$gerror<0.1)/nrow(d3g_short),1)`% of the inferred $\gamma$ were less than 0.1 off (participant ids were `r d3g_short$pID[d3g_short$gerror>=0.1]`). The correlation of $\gamma$ to inferred $\gamma$ was r=`r round(d3g_gcor$estimate[[1]],5)`, p=`r round(d3g_gcor$p.value[1],3)`.
